### 2022-02-22 Code/PointGuardPAR.Rmd
Add files via upload

---
title: "Points Above Replacement"
subtitle: "A New NBA Metric for Player Performance"
author: |
  | Brian Krikorian and Jun Yan
  | brian.krikorian@uconn.edu
  | Department of Statistics, University of Connecticut
date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 11pt
#bibliography: citations.bib
biblio-style: asa
---

```{r data, include=FALSE}
pointGuards <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/PointGuards.csv', stringsAsFactors = TRUE, header = TRUE)
```

```{r initialize variables, echo=FALSE}
position<-list(pointGuards$Pos)
games<-list(pointGuards$G)
minutesPlayed<-list(pointGuards$MP)
fieldGoalPercentage<- list(pointGuards$FG.)
threePointPercentage<-list(pointGuards$X3P.)
twoPointPercentage<-list(pointGuards$X2P.)
effectiveFieldGoalPercentage<-list(pointGuards$eFG.)
freeThrowPercentage<-list(pointGuards$FT.)
offensiveRebounds<-list(pointGuards$ORB)
defensiveRebounds<-list(pointGuards$DRB)
totalRebounds<-list(pointGuards$TRB)
assists<-list(pointGuards$AST)
steals<-list(pointGuards$STL)
blocks<-list(pointGuards$BLK)
turnovers<-list(pointGuards$TOV)
personalFouls<-list(pointGuards$PF)
points<-list(pointGuards$PTS)
player<-list(pointGuards$Player)
pointsPerMinute<-list(pointGuards$PPM)
PER<-list(pointGuards$PER)
trueShooting<-list(pointGuards$TS.)
usagePercentage<-list(pointGuards$USG.)
winShares<-list(pointGuards$WS)
winSharesPer48<-list(pointGuards$WS.48)
boxPlusMinus<-list(pointGuards$BPM)
valueOver<-list(pointGuards$VORP)
```

```{r methods, echo=FALSE}
offensivePoints<-function(effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
+ {(200*effectiveFieldGoalPercentage)+(300*threePointPercentage)+(100*freeThrowPercentage)+(offensiveRebounds)+(3*assists)+(2*points)-(5*turnovers)}
pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
defensivePoints <- function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(2*blocks)-(2*personalFouls)}
pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
positionalAdjustment<-function(minutesPlayed)
+ {((minutesPlayed/48)/72)*(minutesPlayed/2600)}
pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed)
offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
+ {pgOffensivePoints+pgDefensivePoints}
pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+16}
pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(pgOffensiveAndDefensivePoints, pgPositionalAdjustment, pgPointsPerWin)
+ {(pgOffensiveAndDefensivePoints*pgPositionalAdjustment)/pgPointsPerWin}
pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgPositionalAdjustment,pgPointsPerWin)))
print('PAR Data')
print(pgPAR)
```

```{r scaling factors, echo=FALSE}
scaledOffensivePoints<-scale(pgOffensivePoints, center = TRUE, scale = TRUE)
scaledDefensivePoints<-scale(pgDefensivePoints, center = TRUE, scale = TRUE)
scaledPositionalAdjustment<-scale(pgPositionalAdjustment, center = TRUE, scale = TRUE)
scaledPointsPerWin<-scale(pgPointsPerWin, center = TRUE, scale = TRUE)
scaledPAR<-scale(pgPAR, center = TRUE, scale = TRUE)
```

```{r performing regression, echo=FALSE}
PPM<-as.numeric(pointGuards$PPM)
regressionPPMonPAR<-lm(scaledPAR ~ PPM)
print('Regression of PPM(X) on PAR(Y)')
summary(regressionPPMonPAR)

multipleRegression<-lm(scaledPAR ~ pointGuards$PER + pointGuards$WS + pointGuards$BPM + pointGuards$VORP)
print('Multiple Regression: X = PER, WS, BPM, VORP, Y = PAR')
summary(multipleRegression)

nonPARmultipleRegression<-lm(pointGuards$VORP ~ pointGuards$PER + pointGuards$WS + pointGuards$BPM )
print('Multiple Regression: X = PER, WS, BPM, VORP, Y = VORP')
summary(nonPARmultipleRegression)

print('ANOVA of Multiple Regression with PAR as Y')
anova(multipleRegression)

print('RSE of Multiple Regression with PAR as Y')
sigma(multipleRegression)/mean(pgPAR)
print('RSE of Regression of PPM(X) on PAR(Y)')
sigma(regressionPPMonPAR)/mean(pgPAR)
```

Plots
```{r plot1, echo = FALSE}
print('Plots of Multiple Regression with PAR as Y')
plot(multipleRegression)
```
```{r plot2, echo = FALSE}
print('Plots of Regression of PPM (X) on PAR (Y)')
plot(regressionPPMonPAR)
```

### 2022-02-28 Manuscript/PARManuscript.tex
Add files via upload

% Created by Bonita Graham
% Last update: December 2019 By Kestutis Bendinskas
% Authors: 
% Please do not make changes to the preamble until after the solid line of %s.
\documentclass[10pt]{article}
\usepackage[explicit]{titlesec}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage{hyphenat}
\usepackage{ragged2e}
\RaggedRight
% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
\usepackage{garamondx}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amsthm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
\usepackage{booktabs}
% This adjusts the underline to be in keeping with word processors.
\usepackage{soul}
\setul{.6pt}{.4pt}
% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
\usepackage{geometry}
\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\pagenumbering{gobble}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
% These Commands create the label style for tables, figures and equations.
\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
\captionsetup{labelformat=simple, labelsep=period}
\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
\renewcommand{\theequation}{\arabic{equation}}
\makeatletter
\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
\makeatother
\setlength{\intextsep}{10pt}
\setlength{\abovecaptionskip}{2pt}
\setlength{\belowcaptionskip}{-10pt}
\renewcommand{\textfraction}{0.10}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\floatpagefraction}{0.90}
% These commands set the paragraph and line spacing
\titleformat{\section}
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
\titlespacing\section{0pt}{0pt}{-10pt}
\titleformat{\subsection}
  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
\titlespacing\subsection{0pt}{0pt}{-8pt}
\renewcommand{\baselinestretch}{1.15}
% This designs the title display style for the maketitle command
\makeatletter
\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
\begin{flushleft}
\sixteen\bfseries \@title
\medskip
\end{flushleft}
\textit{\@author}
\egroup}
\makeatother
% This styles the bibliography and citations.
%\usepackage[biblabel]{cite}
\usepackage[sort&compress]{natbib}
\setlength\bibindent{2em}
\makeatletter
\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
\makeatother
\renewcommand{\citenumfont}[1]{\textbf{#1}}
\bibpunct{}{}{,~}{s}{,}{,}
\setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{float}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Authors: Add additional packages and new commands here.  
% Limit your use of new commands and special formatting.
% Place your title below. Use Title Capitalization.
\title{Points Above Replacement: A New NBA Metric to Evaluate Player Performance}
% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
\author{
Brian Krikorian*, Jun Yan \\ \medskip 
Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
Students: brian.krikorian@uconn.edu* \\
Mentor: jun.yan@uconn.edu 
}
\pagestyle{empty}
\begin{document}
% Makes the title and author information appear.
\vspace*{.01 in}
\maketitle
\vspace{.12 in}
% Abstracts are required.
\section*{abstract}
% Keywords are required.
\section*{keywords} 
NBA; Basketball; Player Performance; Basketball Metrics;
\vspace{.12 in}
% Start the main part of the manuscript here.
% Comment out section headings if inappropriate to your discipline.
% If you add additional section or subsection headings, use an asterisk * to avoid numbering. 
\section{Introduction}
\section{Literature Review}
\section{Data}
\section{Methods}
\section{Results}
\section{Discussion}
\bibliographystyle{chicago}
\bibliography{citations.bib}
% \section*{acknowledgements}
% The authors thank the University of Connecticut and the UConn Department of Statistics.
%Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '
% The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
% If there is more than one student author, you must move the comment below.
\section*{about the student author}
%\section*{about the student authors}
% The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
\section*{press summary}
\end{document}

### 2022-03-01 Code/PointGuardPAR.Rmd
Add files via upload

@@
 valueOver<-list(pointGuards$VORP)
+teamTotalPoints<-list(pointGuards$TeamTotalPoints)
 ```
@@
 pgOffensivePoints <- mapply(offensivePoints, effectiveFieldGoalPercentage, threePointPercentage, freeThrowPercentage, offensiveRebounds, assists, points, turnovers)
-defensivePoints <- function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
-+ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(2*blocks)-(2*personalFouls)}
+defensivePoints <-function(defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
++ {(2*defensiveRebounds)+(3*totalRebounds)+(5*steals)+(3*blocks)-(3*personalFouls)}
 pgDefensivePoints<-mapply(defensivePoints, defensiveRebounds, totalRebounds, steals, blocks, personalFouls)
-positionalAdjustment<-function(minutesPlayed)
-+ {((minutesPlayed/48)/72)*(minutesPlayed/2600)}
-pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed)
 offensiveAndDefensivePoints<-function(pgOffensivePoints, pgDefensivePoints)
@@
 pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
+positionalAdjustment<-function(minutesPlayed, points, teamTotalPoints)
++ {(minutesPlayed/3456)*(points/teamTotalPoints)}
+pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed, points, teamTotalPoints)
 pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
-+  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+16}
++  {48*((pgOffensiveAndDefensivePoints)/minutesPlayed)*8+72}
 pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
@@
 scaledDefensivePoints<-scale(pgDefensivePoints, center = TRUE, scale = TRUE)
-scaledPositionalAdjustment<-scale(pgPositionalAdjustment, center = TRUE, scale = TRUE)
 scaledPointsPerWin<-scale(pgPointsPerWin, center = TRUE, scale = TRUE)
@@
 summary(regressionPPMonPAR)
+
+print('Regression of PAR(X) on VORP(Y)')
+PARandVORP<-lm(scaledPAR~pointGuards$VORP)
+summary(PARandVORP)
+plot(pointGuards$VORP, scaledPAR)
+
+print('Regression of PAR(X) on BPM(Y)')
+PARandBPM<-lm(scaledPAR~pointGuards$BPM)
+summary(PARandBPM)
+plot(pointGuards$BPM, scaledPAR)
 
@@
 anova(multipleRegression)
-
-print('RSE of Multiple Regression with PAR as Y')
-sigma(multipleRegression)/mean(pgPAR)
-print('RSE of Regression of PPM(X) on PAR(Y)')
-sigma(regressionPPMonPAR)/mean(pgPAR)
 ```

### 2022-03-02 Code/PointGuardPAR.Rmd
Add files via upload

@@
 pgOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,pgOffensivePoints,pgDefensivePoints)
-positionalAdjustment<-function(minutesPlayed, points, teamTotalPoints)
+teamAdjustment<-function(minutesPlayed, points, teamTotalPoints)
 + {(minutesPlayed/3456)*(points/teamTotalPoints)}
-pgPositionalAdjustment<-mapply(positionalAdjustment, minutesPlayed, points, teamTotalPoints)
+pgTeamAdjustment<-mapply(teamAdjustment, minutesPlayed, points, teamTotalPoints)
 pointsPerWin<-function(pgOffensiveAndDefensivePoints, minutesPlayed)
@@
 pgPointsPerWin<-diag(mapply(pointsPerWin, pgOffensiveAndDefensivePoints, minutesPlayed))
-PAR<-function(pgOffensiveAndDefensivePoints, pgPositionalAdjustment, pgPointsPerWin)
-+ {(pgOffensiveAndDefensivePoints*pgPositionalAdjustment)/pgPointsPerWin}
-pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgPositionalAdjustment,pgPointsPerWin)))
+PAR<-function(pgOffensiveAndDefensivePoints, pgTeamAdjustment, pgPointsPerWin)
++ {(pgOffensiveAndDefensivePoints*pgTeamAdjustment)/pgPointsPerWin}
+pgPAR<-diag(diag(mapply(PAR, pgOffensiveAndDefensivePoints,pgTeamAdjustment,pgPointsPerWin)))
 print('PAR Data')

### 2022-03-02 Manuscript/PARManuscript.tex
Add files via upload

@@
 \section*{abstract}
+In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other reason not playing have a significant impact on said prediction.
+Baseball uses a statistic called Wins Above Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player with one who is league average.
+The goal of this paper is to create a similar statistic, called Points Above Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team gains or loses by missing a certain player, and thus having to replace him with one who is "league average".
+The statistic is standardized and adjusted by both position and value to a player's given team.
+The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense and defense, as well as a positional and team adjustment.
+A comparison with the created metric along with other well-known advanced player metrics is done via a multiple regression.
 % Keywords are required.
@@
 \section{Introduction}
+There exists many prediction models for NBA basketball, many with the purpose of anticipating the final score of a given game.
+However, the majority of these models use team average statistics to base their decision, similar to the openWAR method in baseball introduced by Greg Matthews and others.
+However, teams rosters can change every night, and do often.
+When star players are ruled out, players of lower quality take their minutes, and are expected to perform at a lower level.
+When lower level players do not play in a given game, star players are expected to play more minutes, which most likely will cause a slight uptick in performance.
+This reasoning is the cause for the creation of the new metric, PAR.
+The measure of how many points a team will gain or lose if a certain player does not play.
+The metric is created based on the last completed season, the 2020-2021 season, which was cut to 72 games, as opposed to 82, due to the COVID-19 pandemic.
+Future models could be adjusted to a full 82 game season, and automated to update statistics as the season goes on.
+Position and team adjustments allow for a player's value to his specific team to be measured, giving a better expectation for their presence or absence.
+Adjusting to a position allows one to analyze a player based on what his position requires.
+A point guard is expected to pass, shoot three pointers, and get steals more than he is expected to block shots and rebound.
+The opposite is true for centers, so different coefficients are created based on the primary position a player played throughout the season.
+The team adjustment is a function of how many minutes a player played throughout the entire season, and how many of their team's total points were scored by them.
+If a player plays a majority of his team's minutes, and scores a relatively high percentage of his team's points, he will be more valuable to his team, and his team will be hurt more by his absence in a game.
 \section{Literature Review}
 \section{Data}
+All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference website.
+Each teams total points throughout the course of the season were also collected from the Basketball Reference website.
+From the basic statistics, 4 metrics were created in order to calculate PAR.
+Offensive Points is a function of how many points a player will create on offense.
+While the coefficients vary by position, the statistics used are effective field goal percentage, three point percentage, free throw percentage, offensive rebounds, assists, points, and turnovers.
+Similarly, Defensive Points is a function of how many points a player helps prevent while his team is on defense.
+The coefficients also vary by position, but this metric is based on defensive rebounds, total rebounds, steals, blocks, and personal fouls.
+The Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is based on how many minutes a player plays relative to their team, as well as how many points they score relative to their teams total points.
+The last statistic created is Points Per Win, which is based on the average amount of points a player will create in a game.
+This function is based on the sum of Offensive and Defensive Points, and is scaled to incorporate the total number of games, minutes, and players in a season.
+This statistic is very similarly calculated to Runs Per Win in the WAR statistic.
+Given that over the course of a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in terms of strength of schedule.
+Advanced statistics for each player were also collected in order to perform a regression, to see how PAR compares with known and accepted metrics.
+Value Over Replacement Player, also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus Minus, also known as BPM.
+These statistics also help give a relative estimate of a player's value compared to that of an average player, but they translate the statistic to a league average team as well.
+PAR does not do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire league.
+If a player switched teams, his PAR value would most likely change, as his importance to one team may be more or less than it would to another.
+For simplicity, the team that a player played his most games on was taken into consideration for this metric.
+Other statistics used include Player Efficiency Rating, a per-minute rating of player performance, and Win Shares, which estimates the number of wins a player creates for his team throughout the season.
+Due to all of these metrics' relative similarity to PAR, it is suggested that if they are highly correlated with PAR, it is a successful metric.
+However, we expect some differentiation between the metrics, as they all vary slightly in what they attempt to convey.
 \section{Methods}

### 2022-03-19 Code/NBAPARCode.Rmd
Add files via upload

---
title: "Points Above Replacement"
subtitle: "A New NBA Metric for Player Performance"
author: |
  | Brian Krikorian and Jun Yan
  | brian.krikorian@uconn.edu
  | Department of Statistics, University of Connecticut
date: "`r format(Sys.time(), '%d, %B, %Y')`"
documentclass: article
papersize: letter
fontsize: 11pt
#bibliography: citations.bib
biblio-style: asa
---

```{r data, include=FALSE}
league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/League.csv', stringsAsFactors = TRUE, header = TRUE)
```

```{r initialize variables, echo=FALSE}
player<-list(league$Player)
position<-list(league$Pos)
games<-list(league$G)
minutesPlayed<-list(league$MP)
threePointPercentage<-list(league$X3P.)
effectiveFieldGoalPercentage<-list(league$eFG.)
freeThrowPercentage<-list(league$FT.)
offensiveRebounds<-list(league$ORB)
defensiveRebounds<-list(league$DRB)
totalRebounds<-list(league$TRB)
assists<-list(league$AST)
steals<-list(league$STL)
blocks<-list(league$BLK)
turnovers<-list(league$TOV)
personalFouls<-list(league$PF)
points<-list(league$PTS)
PER<-list(league$PER)
trueShooting<-list(league$TS.)
usagePercentage<-list(league$USG.)
winShares<-list(league$WS)
winSharesPer48<-list(league$WS.48)
boxPlusMinus<-list(league$BPM)
valueOver<-list(league$VORP)
teamTotalPoints<-list(league$TeamTotalPoints)
x1<-list(league$X1)
x2<-list(league$X2)
x3<-list(league$X3)
x4<-list(league$X4)
x5<-list(league$X5)
x6<-list(league$X6)
x7<-list(league$X7)
x8<-list(league$X8)
x9<-list(league$X9)
x10<-list(league$X10)
x11<-list(league$X11)
x12<-list(league$X12)
```

```{r methods, echo=FALSE}
offensivePoints<-function(x1, effectiveFieldGoalPercentage, x2, threePointPercentage, x3, freeThrowPercentage, x4, offensiveRebounds, x5, assists, x6, points, x7, turnovers)
+ {(x1*effectiveFieldGoalPercentage)+(x2*threePointPercentage)+(x3*freeThrowPercentage)+(x4*offensiveRebounds)+(x5*assists)+(x6*points)+(x7*turnovers)}
NBAOffensivePoints <- mapply(offensivePoints, x1, effectiveFieldGoalPercentage, x2, threePointPercentage, x3, freeThrowPercentage, x4, offensiveRebounds, x5, assists, x6, points, x7, turnovers)
defensivePoints <-function(x8, defensiveRebounds, x9, totalRebounds, x10, steals, x11, blocks, x12, personalFouls)
+ {(x8*defensiveRebounds)+(x9*totalRebounds)+(x10*steals)+(x11*blocks)+(x12*personalFouls)}
NBADefensivePoints<-mapply(defensivePoints, x8, defensiveRebounds, x9, totalRebounds, x10, steals, x11, blocks, x12, personalFouls)
offensiveAndDefensivePoints<-function(NBAOffensivePoints, NBADefensivePoints)
+ {NBAOffensivePoints+NBADefensivePoints}
NBAOffensiveAndDefensivePoints<-mapply(offensiveAndDefensivePoints,NBAOffensivePoints,NBADefensivePoints)
teamAdjustment<-function(minutesPlayed, points, teamTotalPoints)
+ {(minutesPlayed/3456)*(points/teamTotalPoints)}
NBATeamAdjustment<-mapply(teamAdjustment, minutesPlayed, points, teamTotalPoints)
pointsPerWin<-function(NBAOffensiveAndDefensivePoints, minutesPlayed)
+  {((NBAOffensiveAndDefensivePoints)/minutesPlayed)+2160}
NBAPointsPerWin<-diag(mapply(pointsPerWin, NBAOffensiveAndDefensivePoints, minutesPlayed))
PAR<-function(NBAOffensiveAndDefensivePoints, NBATeamAdjustment, NBAPointsPerWin)
+ {(NBAOffensiveAndDefensivePoints*NBATeamAdjustment)/NBAPointsPerWin}
NBAPAR<-diag(diag(mapply(PAR, NBAOffensiveAndDefensivePoints,NBATeamAdjustment,NBAPointsPerWin)))
print('NBA PAR')
```

```{r scaling factors, echo=FALSE}
scaledOffensivePoints<-scale(NBAOffensivePoints, center = TRUE, scale = TRUE)
scaledDefensivePoints<-scale(NBADefensivePoints, center = TRUE, scale = TRUE)
scaledPointsPerWin<-scale(NBAPointsPerWin, center = TRUE, scale = TRUE)
scaledPAR<-scale(NBAPAR, center = TRUE, scale = TRUE)
```

```{r performing regression, echo=FALSE}
print('Regression of PAR(X) on VORP(Y)')
PARandVORP<-lm(scaledPAR~league$VORP)
summary(PARandVORP)
plot(league$VORP, scaledPAR)

multipleRegression<-lm(scaledPAR ~ league$PER + league$WS + league$BPM + league$VORP)
print('Multiple Regression: X = PER, WS, BPM, VORP, Y = PAR')
summary(multipleRegression)

nonPARmultipleRegression<-lm(league$VORP ~ league$PER + league$WS + league$BPM )
print('Multiple Regression: X = PER, WS, BPM, VORP, Y = VORP')
summary(nonPARmultipleRegression)

print('ANOVA of Multiple Regression with PAR as Y')
anova(multipleRegression)
```

Plots
```{r plot1, echo = FALSE}
print('Plots of Multiple Regression with PAR as Y')
plot(multipleRegression)
```

### 2022-03-21 Manuscript/PARManuscript.tex
Add files via upload

@@
 In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other reason not playing have a significant impact on said prediction.
-Baseball uses a statistic called Wins Above Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player with one who is league average.
-The goal of this paper is to create a similar statistic, called Points Above Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team gains or loses by missing a certain player, and thus having to replace him with one who is "league average".
+Baseball uses a statistic called Wins Above Replacement, or WAR, to tell how many wins a
+team would gain or lose if they replaced a certain player with one who is league average.
+The goal of this paper is to create a similar statistic, called Points Above Replacement, or PAR, that uses statistics from throughout the season to predict how many points a
+team gains or loses by missing a certain player, and thus having to replace him with one who is "league average".
 The statistic is standardized and adjusted by both position and value to a player's given team.
-The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense and defense, as well as a positional and team adjustment.
+The model roughly follows the calculation of WAR in
+baseball, assigning values to points created on offense and defense, as well as a positional and team adjustment.
 A comparison with the created metric along with other well-known advanced player metrics is done via a multiple regression.
@@
 % If you add additional section or subsection headings, use an asterisk * to avoid numbering.
+
 \section{Introduction}
+%Why is this important/interesting? What has been done before on this topic? (Literature Review) What am I introducing that is new? 
 There exists many prediction models for NBA basketball, many with the purpose of anticipating the final score of a given game.
-However, the majority of these models use team average statistics to base their decision, similar to the openWAR method in baseball introduced by Greg Matthews and others.
+However, the majority of these models use team average statistics to base their decision, similar to the openWAR method in baseball
+introduced by Greg Matthews and others.
 However, teams rosters can change every night, and do often.
 When star players are ruled out, players of lower quality take their minutes, and are expected to perform at a lower level.
-When lower level players do not play in a given game, star players are expected to play more minutes, which most likely will cause a slight uptick in performance.
+When lower level players do not
+play in a given game, star players are expected to play more minutes, which most likely will cause a slight uptick in performance.
 This reasoning is the cause for the creation of the new metric, PAR.
-The measure of how many points a team will gain or lose if a certain player does not play.
+The measure of how many points a team will gain or lose if a
+certain player does not play.
 The metric is created based on the last completed season, the 2020-2021 season, which was cut to 72 games, as opposed to 82, due to the COVID-19 pandemic.
-Future models could be adjusted to a full 82 game season, and automated to update statistics as the season goes on.
+Future models could be adjusted to a full 82 game season, and
+automated to update statistics as the season goes on.
 Position and team adjustments allow for a player's value to his specific team to be measured, giving a better expectation for their presence or absence.
-Adjusting to a position allows one to analyze a player based on what his position requires.
+Adjusting to a position allows one to analyze a player
+based on what his position requires.
 A point guard is expected to pass, shoot three pointers, and get steals more than he is expected to block shots and rebound.
-The opposite is true for centers, so different coefficients are created based on the primary position a player played throughout the season.
+The opposite is true for centers, so different coefficients are created based on the primary position
+a player played throughout the season.
 The team adjustment is a function of how many minutes a player played throughout the entire season, and how many of their team's total points were scored by them.
-If a player plays a majority of his team's minutes, and scores a relatively high percentage of his team's points, he will be more valuable to his team, and his team will be hurt more by his absence in a game.
-\section{Literature Review}
+If a player plays a majority of his team's minutes, and
+scores a relatively high percentage of his team's points, he will be more valuable to his team, and his team will be hurt more by his absence in a game.
+
 \section{Data}
@@
 Each teams total points throughout the course of the season were also collected from the Basketball Reference website.
+
 From the basic statistics, 4 metrics were created in order to calculate PAR.
 Offensive Points is a function of how many points a player will create on offense.
-While the coefficients vary by position, the statistics used are effective field goal percentage, three point percentage, free throw percentage, offensive rebounds, assists, points, and turnovers.
+While the coefficients vary by position, the statistics used are effective field goal percentage, three point
+percentage, free throw percentage, offensive rebounds, assists, points, and turnovers.
 Similarly, Defensive Points is a function of how many points a player helps prevent while his team is on defense.
-The coefficients also vary by position, but this metric is based on defensive rebounds, total rebounds, steals, blocks, and personal fouls.
-The Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is based on how many minutes a player plays relative to their team, as well as how many points they score relative to their teams total points.
+The coefficients also vary by position, but this metric is based
+on defensive rebounds, total rebounds, steals, blocks, and personal fouls.
+The Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is based on how many minutes a player plays relative to their team, as well
+as how many points they score relative to their teams total points.
 The last statistic created is Points Per Win, which is based on the average amount of points a player will create in a game.
-This function is based on the sum of Offensive and Defensive Points, and is scaled to incorporate the total number of games, minutes, and players in a season.
-This statistic is very similarly calculated to Runs Per Win in the WAR statistic.
+This function is based on the sum of Offensive and Defensive Points,
+and is scaled to incorporate the total number of games, minutes, and players in a season. This statistic is very similarly calculated to Runs Per Win in the WAR statistic.
+
 Given that over the course of a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in terms of strength of schedule.
-Advanced statistics for each player were also collected in order to perform a regression, to see how PAR compares with known and accepted metrics.
+Advanced statistics for each player were also collected in order to perform a regression, to
+see how PAR compares with known and accepted metrics.
 Value Over Replacement Player, also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus Minus, also known as BPM.
-These statistics also help give a relative estimate of a player's value compared to that of an average player, but they translate the statistic to a league average team as well.
-PAR does not do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire league.
+These statistics also help give a
+relative estimate of a player's value compared to that of an average player, but they translate the statistic to a league average team as well.
+PAR does not do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire
+league.
 If a player switched teams, his PAR value would most likely change, as his importance to one team may be more or less than it would to another.
@@
 Other statistics used include Player Efficiency Rating, a per-minute rating of player performance, and Win Shares, which estimates the number of wins a player creates for his team throughout the season.
-Due to all of these metrics' relative similarity to PAR, it is suggested that if they are highly correlated with PAR, it is a successful metric.
+Due to all of these metrics' relative similarity to PAR, it is
+suggested that if they are highly correlated with PAR, it is a successful metric.
 However, we expect some differentiation between the metrics, as they all vary slightly in what they attempt to convey.
+The relative correlation between all these statistics shows that
+PAR is related to other advanced metrics analyzing player efficiency, but also that it introduces something new in basketball statistics.
+
 \section{Methods}
+The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but also took influences from other advanced basketball statistics.
+WAR is based on Offensive and Defensive Runs, which are calculated subjectively via
+attributes of the game such as hitting, base running, fielding, and so forth.
+The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and Defensive Runs.
+Thus, there are actually an infinite different kinds of WAR in baseball,
+depending on which method of calculating Offensive and Defensive Runs is used.
+Similarly, PAR is created by calculating Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how many he prevents the other
+team from scoring.
+Using the basic offensive statistics of Effective Field Goal Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and Turnovers, we assign a coefficient to them based on how important they are for
+a given position.
+Point guards are expected to pass more than centers, and a point guard's passing ability has more value to his team than a center, so more weight is placed on that statistic for point guards.
+This goes for all positions, and a coefficient matrix of a
+constant scale is created.
+That is to say, assists have a coefficient from point guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2.
+The coefficient by position method is one similar to that of Box Plus Minus,
+another advanced NBA metric.
+The position a player was assigned for the calculation was the position where he played the most minutes throughout the 2020-2021 season.
+This coefficient method gives a clean scaling into the calculation of Offensive Points.
+Some statistics, such as Points and Effective Field Goal Percentage, are equally important, regardless of the position of a given player.
+Thus, these statistics have a constant coefficient that does not change.
+Once all coefficients were applied to all statistics, the
+sum was taken to give Offensive Points.
+The exact same method was applied to the Defensive Points calculation, but used the basic defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls.
+As turnovers and personal
+fouls are not desirable amongst players, the coefficients for these statistics is negative, which allows for a scale of not only the good a player does, but also what they do poorly.
+This coefficient method is similar to the Positional Adjustment metric applied in WAR
+calculation, which seeks to adjust a player's importance based on what is expected of their position.
+
+The next step was creating a Team Adjustment statistic.
+As stated before, the PAR metric seeks to anticipate how valuable a player is to their given team, rather than as an average of the entire league.
+This gives more of an insight of how a team will fare without
+a certain player.
+We expect this statistic to change if a player were to switch teams.
+This is similar to the League Adjustment in WAR calculation, where a player's value is adjusted based on whether he plays in the American League or the National League.
+The
+Eastern and Western Conferences in the NBA have much less disparity compared to the MLB, and each conference plays each other much more frequently, so we instead change this to adjust a player's value to his specific team.
+The team assigned to a given
+player was the team where he played the most games during the 2020-2021 season.
+If a player had played an even amount of games for 2 separate teams, the team the player had played the most minutes for was assigned as his team.
+The Team Adjustment
+statistic is then calculated by taking the total minutes a player was on the court during the entire season, and diving it by a constant of 3,456 (the maximum number of minutes a player could have played during the shortened season, 48 minutes per game
+multiplied by 72 games).
+Then, the percentage of points a player scored for his team (player's total points divided by team's total points throughout the season) was calculated, and the two results were multiplied together.
+As a player cannot play 100 percent of
+his team's minutes, or score 100 percent of his team's points, the result is a number between 0 and 1.
+A similar adjustment is also used in the calculation of Box Plus Minus, which is a key factor in calculating Value Over Replacement Player, two of the advanced
+metrics PAR will be compared against.
+The goal of this adjustment is to give less of a penalty to players who play a majority of their team's minutes, and score a majority of their team's points.
+This helps truly elite players stand out amongst the pack, as well as
+players who may not be the best of the best, but matter more to their team specifically than in the grand scheme of things.
+
+Lastly, WAR implements a Runs Per Win statistic, which gives a basic idea of how many runs are needed for a win in the MLB.
+Similarly, a Points Per Win statistic is created for the NBA, which allows a scaling down of the PAR statistic.
+We calculate this via the
+combined Offensive and Defensive Points statistic for a player divided by the number of minutes he played, then adding 2,160 (72 games per season times 30 teams in the NBA, thus, the total number of chances to win throughout the season).
+This gives a basic
+metric of a players points created as a function of how many minutes he played, and allows us to even the metric out a bit more from star players to role players.
+This statistic serves as the denominator of our PAR calculation.
+
+Once all supporting statistics of PAR have been created, all that is left to do is combine them to achieve our PAR values for each player in the NBA. The formula for PAR is as follows:
+
+\begin{equation}
+((Offensive Points + DefensivePoints) * (Team Adjustment))/(Points Per Win)
+\end{equation}
+
+This gives a good idea of how many points a player accounts for during a game, how important that is for his given team, and how important it is compared to all other players.
+The last step is to standardize this PAR statistic, so that the mean is 0, and the
+standard deviation is 1.
+Logically, this helps the idea of the metric in the sense that a perfectly league average player should have a PAR of 0, and his presence or absence from his team neither adds nor subtracts value.
+Thus, we have created a new NBA player
+metric, Points Above Replacement, PAR.
+
 \section{Results}
+% Multiple Regression
+% Analyze Graphs of PAR, filter by position perhaps?
+% Any other tests that should be done?
+
 \section{Discussion}
+
 \bibliographystyle{chicago}
-\bibliography{citations.bib}
+%\bibliography{citations.bib}
 % \section*{acknowledgements}
-% The authors thank the University of Connecticut and the UConn Department of Statistics.
+The authors thank the University of Connecticut and the UConn Department of Statistics.
 %Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '
@@
 %\section*{about the student authors}
+Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.
 % The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.

### 2022-03-21 Manuscript/PARManuscript.tex
Add files via upload

@@
 \vspace{.12 in}
+
 % Abstracts are required.
@@
 A comparison with the created metric along with other well-known advanced player metrics is done via a multiple regression.
+
 % Keywords are required.
@@
 \section{Data}
+% Include basic graphics here?
 All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference website.
@@
 \section{Methods}
+% Should dive more in depth about how everything was obtained, calculated, etc.
 The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but also took influences from other advanced basketball statistics.
@@
 \section{Discussion}
+% Analyzing entire study, show how you can use PAR now, did it achieve the overall goal I was looking for?
+% Talk about drawbacks, what could be improved, etc.
 
@@
 The authors thank the University of Connecticut and the UConn Department of Statistics.
+
 %Note correct LaTeX quotations above. Do not use the " symbol, but rather double ` followed by double '
+
 % The About the Student Author section is NOT optional.  Write a paragraph about the student; see previous journal editions for examples.
@@
 \section*{about the student author}
-%\section*{about the student authors}
 Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.
+
 % The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
 \section*{press summary}
+
 \end{document}

### 2022-03-28 Manuscript/Manuscript.tex
Add files via upload
Update Manuscript.tex

--- 2022-03-21 Manuscript/PARManuscript.tex
@@
-% Created by Bonita Graham
-% Last update: December 2019 By Kestutis Bendinskas
-% Authors: 
-% Please do not make changes to the preamble until after the solid line of %s.
-\documentclass[10pt]{article}
-\usepackage[explicit]{titlesec}
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{1em}
-\usepackage{hyphenat}
-\usepackage{ragged2e}
-\RaggedRight
-% These commands change the font. If you do not have Garamond on your computer, you will need to install it.
-\usepackage{garamondx}
-\usepackage[T1]{fontenc}
-\usepackage{amsmath, amsthm}
-\usepackage{graphicx}
-\usepackage{hyperref}
+\documentclass[12pt]{article}
+\usepackage[margin=1in]{geometry}
+
+\usepackage{xr-hyper}
+\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
+\usepackage{listings}
+\usepackage{rotating, graphicx}
+\usepackage{booktabs, natbib}
+
+\usepackage{amsmath, enumerate, quoting, amssymb, subfigure, url}
+
+\usepackage{color}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand{\gv}[1]{\textcolor{blue}{(GV: #1)}}
+\DeclareMathOperator*{\argmin}{arg\,min}
+\DeclareMathOperator*{\cov}{Cov}
+\DeclareMathOperator*{\corr}{Corr}
+
+\usepackage{xr}
+\externaldocument{isgee}
+\externaldocument{supp}
+
+% remove left indentation in itemize
+\usepackage{enumitem}
+\setlist[itemize]{leftmargin=*}
+
 \usepackage{xcolor}
-\newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
-\usepackage{booktabs}
-% This adjusts the underline to be in keeping with word processors.
-\usepackage{soul}
-\setul{.6pt}{.4pt}
-% The following sets margins to 1 in. on top and bottom and .75 in on left and right, and remove page numbers.
-\usepackage{geometry}
-\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\pagenumbering{gobble}
-\renewcommand{\headrulewidth}{0.0pt}
-\renewcommand{\footrulewidth}{0.0pt}
-% These Commands create the label style for tables, figures and equations.
-\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
-\captionsetup{labelformat=simple, labelsep=period}
-\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
-\renewcommand{\theequation}{\arabic{equation}}
-\makeatletter
-\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
-\makeatother
-\setlength{\intextsep}{10pt}
-\setlength{\abovecaptionskip}{2pt}
-\setlength{\belowcaptionskip}{-10pt}
-\renewcommand{\textfraction}{0.10}
-\renewcommand{\topfraction}{0.85}
-\renewcommand{\bottomfraction}{0.85}
-\renewcommand{\floatpagefraction}{0.90}
-% These commands set the paragraph and line spacing
-\titleformat{\section}
-  {\normalfont}{\thesection}{1em}{\MakeUppercase{\textbf{#1}}}
-\titlespacing\section{0pt}{0pt}{-10pt}
-\titleformat{\subsection}
-  {\normalfont}{\thesubsection}{1em}{\textit{#1}}
-\titlespacing\subsection{0pt}{0pt}{-8pt}
-\renewcommand{\baselinestretch}{1.15}
-% This designs the title display style for the maketitle command
-\makeatletter
-\newcommand\sixteen{\@setfontsize\sixteen{17pt}{6}}
-\renewcommand{\maketitle}{\bgroup\setlength{\parindent}{0pt}
-\begin{flushleft}
-\sixteen\bfseries \@title
-\medskip
-\end{flushleft}
-\textit{\@author}
-\egroup}
-\makeatother
-% This styles the bibliography and citations.
-%\usepackage[biblabel]{cite}
-\usepackage[sort&compress]{natbib}
-\setlength\bibindent{2em}
-\makeatletter
-\renewcommand\@biblabel[1]{\textbf{#1.}\hfill}
-\makeatother
-\renewcommand{\citenumfont}[1]{\textbf{#1}}
-\bibpunct{}{}{,~}{s}{,}{,}
-\setlength{\bibsep}{0pt plus 0.3ex}
-\usepackage{float}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Authors: Add additional packages and new commands here.  
-% Limit your use of new commands and special formatting.
-% Place your title below. Use Title Capitalization.
+\newcommand{\jy}[1]{\textcolor{red}{(JY: #1)}}
+
+% graph path
+\graphicspath{{./figs/}}
+
+\quotingsetup{leftmargin = 0pt}
+
+\newenvironment{comment}%
+{\begin{quoting}\noindent\small\it\ignorespaces%
+  }{\end{quoting}}
  \title{Points Above Replacement: A New NBA Metric to Evaluate Player Performance}
-% Add author information below. Communicating author is indicated by an asterisk, the affiliation is shown by superscripted lower case letter if several affiliations need to be noted.
 \author{
@@
 }
-\pagestyle{empty}
 \begin{document}
-% Makes the title and author information appear.
-\vspace*{.01 in}
-\maketitle
-\vspace{.12 in}
 
@@
 % Any other tests that should be done?
+First, the top 10 players in terms of PAR in the league will be analyzed. Then, the top 10 PAR values at each position will be evaluated.
+%NBA PAR Ranking
+As can be seen, one player rises above all others in both PAR and VORP.
+That player is Nikola Jokic of the Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP season was.
+Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was doing it from the center position.
+Having a center that has the ability to perform in all aspects of the game, even those that his position does not require, proves his value to his team, which is why his value is so much higher in both the new PAR metric, and the accepted VORP metric.
+%Point Guard PAR Ranking
+%Shooting Guard PAR Ranking
+%Small Forward PAR Ranking
+%Power Forward PAR Ranking
+%Center PAR Ranking
+
+PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the multiple regression on PAR.
+These include Player Efficiency Rating, Win Shares, Box Plus Minus, and Value Over Replacement Player
+%PAR vs. PER
+%PAR vs. WS
+%PAR vs. BPM
+%PAR vs. VORP
 
@@
 % Talk about drawbacks, what could be improved, etc.
+Ultimately, the goal of this statistic is to allow a reader to gague a player's value to his team based on a league average player.
+As previously stated, the metric is adjusted so that a league average player has a PAR value of 0.
+Based on all other players' PAR values, we can create a sort of "legend", a rough guideline for what a player's role will be based on the threshold his PAR value falls under.
 

### 2022-03-29 Manuscript/Manuscript.tex
Update Manuscript.tex

@@
 First, the top 10 players in terms of PAR in the league will be analyzed. Then, the top 10 PAR values at each position will be evaluated.
-%NBA PAR Ranking
+\begin{NBAtable}[tbp]
+  \caption{PAR Values from the Entire NBA)
+  \label{tab:NBAtable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Position & Team & PAR\\
+  \midrule
+ 1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
+  \midrule
+ 2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
+  \midrule
+ 3 & Julius Randle & PF & New York Knicks & 6.49\\
+  \midrule
+ 4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
+  \midrule
+ 5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
+  \midrule
+ 6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
+  \midrule
+ 7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
+  \midrule
+ 8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
+  \midrule
+ 9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
+  \midrule
+ 10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
+  \bottomrule
+\end{tabular}
+\end{NBAtable}
+
 As can be seen, one player rises above all others in both PAR and VORP.
@@
 Having a center that has the ability to perform in all aspects of the game, even those that his position does not require, proves his value to his team, which is why his value is so much higher in both the new PAR metric, and the accepted VORP metric.
-%Point Guard PAR Ranking
-%Shooting Guard PAR Ranking
-%Small Forward PAR Ranking
-%Power Forward PAR Ranking
-%Center PAR Ranking
+This logic applies to Nikola Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well.
+While they might not be considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, that can do anything on the court, and thus they are rewarded with a high PAR value.
+This makes sense, as without these players, a lot of the statistics their team accumulates are gone, so while they may not have as much value in the grand scheme of the NBA, they were very much the most valuable players for their teams.
+Another key thing to note is that some players, such as LeBron James, have a lower PAR than expected, and this could be due to the fact that they played most frequently in a position that did not match their skill set.
+LeBron James played primarily as a point guard, but his skillset matches that of a small forward or power forward.
+Thus, his strengths are not adequately measured, as he is essentially being played "out of position".
+\begin{PGtable}[tbp]
+
+  \caption{PAR Values from all Point Guards)
+  \label{tab:PGtable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Team & PAR\\
+  \midrule
+ 1 & Luka Doncic & Dallas Mavericks & 4.61\\
+  \midrule
+ 2 & Damian Lillard & Portland Trail Blazers & 4.47\\
+  \midrule
+ 3 & Stephen Curry & Golden State Warriors & 4.17\\
+  \midrule
+ 4 & Russell Westbrook & Washington Wizards & 4.05\\
+  \midrule
+ 5 & Trae Young & Atlanta Hawks & 2.69\\
+  \midrule
+ 6 & De'Aaron Fox & Sacramento Kings & 1.94\\
+  \midrule
+ 7 & Chris Paul & Phoenix Suns & 1.93\\
+  \midrule
+ 8 & Kyrie Irving & Brooklyn Nets & 1.74\\
+  \midrule
+ 9 & Dejounte Murray & San Antonio Spurs & 1.64\\
+  \midrule
+ 10 & Ja Morant & Memphis Grizzlies & 1.45\\
+  \bottomrule
+\end{tabular}
+\end{PGtable}
+
+\begin{SGtable}[tbp]
+  \caption{PAR Values from all Shooting Guards)
+  \label{tab:SGtable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Team & PAR\\
+  \midrule
+ 1 & Bradley Beal & Washington Wizards & 3.17\\
+  \midrule
+ 2 & Devin Booker & Phoenix Suns & 2.74\\
+  \midrule
+ 3 & Terry Rozier & Charlotte Hornets & 2.59\\
+  \midrule
+ 4 & Zach Lavine & Chicago Bulls & 2.29\\
+  \midrule
+ 5 & RJ Barrett & New York Knicks & 2.28\\
+  \midrule
+ 6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
+  \midrule
+ 7 & Jaylen Brown & Boston Celtics & 1.87\\
+  \midrule
+ 8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
+  \midrule
+ 9 & Buddy Hield & Sacramento Kings & 1.72\\
+  \midrule
+ 10 & Norman Powell & Toronto Raptors & 1.37\\
+  \bottomrule
+\end{tabular}
+\end{SGtable}
+
+\begin{SFtable}[tbp]
+  \caption{PAR Values from all Small Forwards)
+  \label{tab:SFtable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Team & PAR\\
+  \midrule
+ 1 & Jayson Tatum & Boston Celtics & 3.96\\
+  \midrule
+ 2 & Khris Middleton & Milwaukee Bucks & 2.39\\
+  \midrule
+ 3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
+  \midrule
+ 4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
+  \midrule
+ 5 & Paul George & Los Angeles Clippers & 1.44\\
+  \midrule
+ 6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
+  \midrule
+ 7 & Jimmy Butler & Miami Heat & 1.41\\
+  \midrule
+ 8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
+  \midrule
+ 9 & Mikal Bridges & Phoenix Suns & 1.19\\
+  \midrule
+ 10 & Jerami Grant & Detroit Pistons & 1.14\\
+  \bottomrule
+\end{tabular}
+\end{SFtable}
+
+\begin{PFtable}[tbp]
+  \caption{PAR Values from all Power Forwards)
+  \label{tab:PFtable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Team & PAR\\
+  \midrule
+ 1 & Julius Randle & New York Knicks & 6.49\\
+  \midrule
+ 2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
+  \midrule
+ 3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
+  \midrule
+ 4 & Zion Williamson & New Orleans Pelicans & 3.07\\
+  \midrule
+ 5 & Andrew Wiggins & Golden State Warriors & 2.26\\
+  \midrule
+ 6 & Demar Derozan & San Antonio Spurs & 1.88\\
+  \midrule
+ 7 & Tobias Harris & Philadelphia 76ers & 1.87\\
+  \midrule
+ 8 & Pascal Siakam & Toronto Raptors & 1.72\\
+  \midrule
+ 9 & John Collins & Atlanta Hawks & 1.35\\
+  \midrule
+ 10 & Harrison Barnes & Sacramento Kings & 1.11\\
+  \bottomrule
+\end{tabular}
+\end{PFtable}
+
+\begin{Ctable}[tbp]
+  \caption{PAR Values from all Centers)
+  \label{tab:Ctable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Rank & Player & Team & PAR\\
+  \midrule
+ 1 & Nikola Jokic & Denver Nuggets & 7.69\\
+  \midrule
+ 2 & Nikola Vucevic & Orlando Magic & 6.55\\
+  \midrule
+ 3 & Rudy Gobert & Utah Jazz & 3.10\\
+  \midrule
+ 4 & Bam Adebayo & Miami Heat & 2.78\\
+  \midrule
+ 5 & Joel Embiid & Philadelphia 76ers & 2.26\\
+  \midrule
+ 6 & Clint Capela & Atlanta Hawks & 2.25\\
+  \midrule
+ 7 & DeAndre Ayton & Phoenix Suns & 2.11\\
+  \midrule
+ 8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
+  \midrule
+ 9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
+  \midrule
+ 10 & Kelly Olynyk & Miami Heat & 1.39\\
+  \bottomrule
+\end{tabular}
+\end{Ctable}
 

### 2022-03-29 Manuscript/Manuscript.tex
Add files via upload

@@
 
-\usepackage{amsmath, enumerate, quoting, amssymb, subfigure, url}
+\usepackage{amsmath, enumerate, quoting, subfigure, amssymb, url}
 
@@
 \usepackage{xr}
-\externaldocument{isgee}
-\externaldocument{supp}
+%\externaldocument{isgee}
+%\externaldocument{supp}
 
@@
 \graphicspath{{./figs/}}
+
+\usepackage{geometry}
+\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
+
+\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
+\captionsetup{labelformat=simple, labelsep=period}
+\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
+\renewcommand{\theequation}{\arabic{equation}}
+\makeatletter
+\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
+\makeatother
+\setlength{\intextsep}{10pt}
+\setlength{\abovecaptionskip}{2pt}
+\setlength{\belowcaptionskip}{-10pt}
+\renewcommand{\textfraction}{0.10}
+\renewcommand{\topfraction}{0.85}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\floatpagefraction}{0.90}
 
@@
 % Abstracts are required.
-\section*{abstract}
-In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other reason not playing have a significant impact on said prediction.
-Baseball uses a statistic called Wins Above Replacement, or WAR, to tell how many wins a
-team would gain or lose if they replaced a certain player with one who is league average.
-The goal of this paper is to create a similar statistic, called Points Above Replacement, or PAR, that uses statistics from throughout the season to predict how many points a
-team gains or loses by missing a certain player, and thus having to replace him with one who is "league average".
-The statistic is standardized and adjusted by both position and value to a player's given team.
-The model roughly follows the calculation of WAR in
-baseball, assigning values to points created on offense and defense, as well as a positional and team adjustment.
-A comparison with the created metric along with other well-known advanced player metrics is done via a multiple regression.
+\section*{Abstract}
+In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other 
+reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above 
+Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player 
+with one who is league average. The goal of this paper is to create a similar statistic, called Points Above 
+Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team 
+gains or loses by missing a certain player, and thus having to replace him with one who is "league 
+average". The statistic is standardized and adjusted by both position and value to a player's given team. 
+The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense 
+and defense, as well as a positional and team adjustment. A comparison with the created metric along with 
+other well-known advanced player metrics is done via a multiple regression.
 
 % Keywords are required.
-\section*{keywords} 
+\section*{Keywords} 
 NBA; Basketball; Player Performance; Basketball Metrics;
@@
 %Why is this important/interesting? What has been done before on this topic? (Literature Review) What am I introducing that is new? 
-There exists many prediction models for NBA basketball, many with the purpose of anticipating the final score of a given game.
-However, the majority of these models use team average statistics to base their decision, similar to the openWAR method in baseball
-introduced by Greg Matthews and others.
-However, teams rosters can change every night, and do often.
-When star players are ruled out, players of lower quality take their minutes, and are expected to perform at a lower level.
-When lower level players do not
-play in a given game, star players are expected to play more minutes, which most likely will cause a slight uptick in performance.
-This reasoning is the cause for the creation of the new metric, PAR.
-The measure of how many points a team will gain or lose if a
-certain player does not play.
-The metric is created based on the last completed season, the 2020-2021 season, which was cut to 72 games, as opposed to 82, due to the COVID-19 pandemic.
-Future models could be adjusted to a full 82 game season, and
-automated to update statistics as the season goes on.
-Position and team adjustments allow for a player's value to his specific team to be measured, giving a better expectation for their presence or absence.
-Adjusting to a position allows one to analyze a player
-based on what his position requires.
-A point guard is expected to pass, shoot three pointers, and get steals more than he is expected to block shots and rebound.
-The opposite is true for centers, so different coefficients are created based on the primary position
-a player played throughout the season.
-The team adjustment is a function of how many minutes a player played throughout the entire season, and how many of their team's total points were scored by them.
-If a player plays a majority of his team's minutes, and
-scores a relatively high percentage of his team's points, he will be more valuable to his team, and his team will be hurt more by his absence in a game.
+There exists many prediction models for NBA basketball, many with the purpose of anticipating the final 
+score of a given game. However, the majority of these models use team average statistics to base their 
+decision, similar to the openWAR method in baseball introduced by Greg Matthews and others. However, 
+teams rosters can change every night, and do often. When star players are ruled out, players of lower 
+quality take their minutes, and are expected to perform at a lower level. When lower level players do not 
+play in a given game, star players are expected to play more minutes, which most likely will cause a slight 
+uptick in performance. This reasoning is the cause for the creation of the new metric, PAR. The measure of 
+how many points a team will gain or lose if a certain player does not play. The metric is created based on 
+the last completed season, the 2020-2021 season, which was cut to 72 games, as opposed to 82, due to 
+the COVID-19 pandemic. Future models could be adjusted to a full 82 game season, and automated to 
+update statistics as the season goes on. Position and team adjustments allow for a player's value to his 
+specific team to be measured, giving a better expectation for their presence or absence. Adjusting to a 
+position allows one to analyze a player based on what his position requires. A point guard is expected to 
+pass, shoot three pointers, and get steals more than he is expected to block shots and rebound. The 
+opposite is true for centers, so different coefficients are created based on the primary position a player 
+played throughout the season. The team adjustment is a function of how many minutes a player played 
+throughout the entire season, and how many of their team's total points were scored by them. If a player 
+plays a majority of his team's minutes, and scores a relatively high percentage of his team's points, he will 
+be more valuable to his team, and his team will be hurt more by his absence in a game.
 
@@
 % Include basic graphics here?
-All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference website.
-Each teams total points throughout the course of the season were also collected from the Basketball Reference website.
-
-From the basic statistics, 4 metrics were created in order to calculate PAR.
-Offensive Points is a function of how many points a player will create on offense.
-While the coefficients vary by position, the statistics used are effective field goal percentage, three point
-percentage, free throw percentage, offensive rebounds, assists, points, and turnovers.
-Similarly, Defensive Points is a function of how many points a player helps prevent while his team is on defense.
-The coefficients also vary by position, but this metric is based
-on defensive rebounds, total rebounds, steals, blocks, and personal fouls.
-The Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is based on how many minutes a player plays relative to their team, as well
-as how many points they score relative to their teams total points.
-The last statistic created is Points Per Win, which is based on the average amount of points a player will create in a game.
-This function is based on the sum of Offensive and Defensive Points,
-and is scaled to incorporate the total number of games, minutes, and players in a season. This statistic is very similarly calculated to Runs Per Win in the WAR statistic.
-
-Given that over the course of a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in terms of strength of schedule.
-Advanced statistics for each player were also collected in order to perform a regression, to
-see how PAR compares with known and accepted metrics.
-Value Over Replacement Player, also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus Minus, also known as BPM.
-These statistics also help give a
-relative estimate of a player's value compared to that of an average player, but they translate the statistic to a league average team as well.
-PAR does not do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire
-league.
-If a player switched teams, his PAR value would most likely change, as his importance to one team may be more or less than it would to another.
-For simplicity, the team that a player played his most games on was taken into consideration for this metric.
-Other statistics used include Player Efficiency Rating, a per-minute rating of player performance, and Win Shares, which estimates the number of wins a player creates for his team throughout the season.
-Due to all of these metrics' relative similarity to PAR, it is
-suggested that if they are highly correlated with PAR, it is a successful metric.
-However, we expect some differentiation between the metrics, as they all vary slightly in what they attempt to convey.
-The relative correlation between all these statistics shows that
-PAR is related to other advanced metrics analyzing player efficiency, but also that it introduces something new in basketball statistics.
+All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference 
+website. Each teams total points throughout the course of the season were also collected from the 
+Basketball Reference website. From the basic statistics, 4 metrics were created in order to calculate PAR. 
+Offensive Points is a function of how many points a player will create on offense. While the coefficients vary 
+by position, the statistics used are effective field goal percentage, three point percentage, free throw 
+percentage, offensive rebounds, assists, points, and turnovers. Similarly, Defensive Points is a function of 
+how many points a player helps prevent while his team is on defense. The coefficients also vary by position, 
+but this metric is based on defensive rebounds, total rebounds, steals, blocks, and personal fouls. The 
+Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is 
+based on how many minutes a player plays relative to their team, as well as how many points they score 
+relative to their teams total points. The last statistic created is Points Per Win, which is based on the 
+average amount of points a player will create in a game. This function is based on the sum of Offensive and 
+Defensive Points, and is scaled to incorporate the total number of games, minutes, and players in a season. 
+This statistic is very similarly calculated to Runs Per Win in the WAR statistic. Given that over the course of 
+a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in 
+terms of strength of schedule. Advanced statistics for each player were also collected in order to perform a 
+regression, to see how PAR compares with known and accepted metrics. Value Over Replacement Player, 
+also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus 
+Minus, also known as BPM. These statistics also help give a relative estimate of a player's value compared 
+to that of an average player, but they translate the statistic to a league average team as well. PAR does not 
+do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire 
+league. If a player switched teams, his PAR value would most likely change, as his importance to one team 
+may be more or less than it would to another. For simplicity, the team that a player played his most games 
+on was taken into consideration for this metric. Other statistics used include Player Efficiency Rating, a 
+per-minute 
+rating of player performance, and Win Shares, which estimates the number of wins a player creates 
+for his team throughout the season. Due to all of these metrics' relative similarity to PAR, it is suggested 
+that if they are highly correlated with PAR, it is a successful metric. However, we expect some differentiation 
+between the metrics, as they all vary slightly in what they attempt to convey. The relative correlation 
+between all these statistics shows that PAR is related to other advanced metrics analyzing player efficiency, 
+but also that it introduces something new in basketball statistics.
 
@@
 % Should dive more in depth about how everything was obtained, calculated, etc.
-The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but also took influences from other advanced basketball statistics.
-WAR is based on Offensive and Defensive Runs, which are calculated subjectively via
-attributes of the game such as hitting, base running, fielding, and so forth.
-The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and Defensive Runs.
-Thus, there are actually an infinite different kinds of WAR in baseball,
-depending on which method of calculating Offensive and Defensive Runs is used.
-Similarly, PAR is created by calculating Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how many he prevents the other
-team from scoring.
-Using the basic offensive statistics of Effective Field Goal Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and Turnovers, we assign a coefficient to them based on how important they are for
-a given position.
-Point guards are expected to pass more than centers, and a point guard's passing ability has more value to his team than a center, so more weight is placed on that statistic for point guards.
-This goes for all positions, and a coefficient matrix of a
-constant scale is created.
-That is to say, assists have a coefficient from point guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2.
-The coefficient by position method is one similar to that of Box Plus Minus,
-another advanced NBA metric.
-The position a player was assigned for the calculation was the position where he played the most minutes throughout the 2020-2021 season.
-This coefficient method gives a clean scaling into the calculation of Offensive Points.
-Some statistics, such as Points and Effective Field Goal Percentage, are equally important, regardless of the position of a given player.
-Thus, these statistics have a constant coefficient that does not change.
-Once all coefficients were applied to all statistics, the
-sum was taken to give Offensive Points.
-The exact same method was applied to the Defensive Points calculation, but used the basic defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls.
-As turnovers and personal
-fouls are not desirable amongst players, the coefficients for these statistics is negative, which allows for a scale of not only the good a player does, but also what they do poorly.
-This coefficient method is similar to the Positional Adjustment metric applied in WAR
-calculation, which seeks to adjust a player's importance based on what is expected of their position.
+The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but 
+also took influences from other advanced basketball statistics. WAR is based on Offensive and Defensive 
+Runs, which are calculated subjectively via attributes of the game such as hitting, base running, fielding, 
+and so forth. The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and 
+Defensive Runs. Thus, there are actually an infinite different kinds of WAR in baseball, depending on which 
+method of calculating Offensive and Defensive Runs is used. Similarly, PAR is created by calculating 
+Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how 
+many he prevents the other team from scoring. Using the basic offensive statistics of Effective Field Goal 
+Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and 
+Turnovers, we assign a coefficient to them based on how important they are for a given position. Point 
+guards are expected to pass more than centers, and a point guard's passing ability has more value to his 
+team than a center, so more weight is placed on that statistic for point guards. This goes for all positions, 
+and a coefficient matrix of a constant scale is created. That is to say, assists have a coefficient from point 
+guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2. 
+The coefficient by position method is one similar to that of Box Plus Minus, another advanced NBA metric. 
+The position a player was assigned for the calculation was the position where he played the most minutes 
+throughout the 2020-2021 season. This coefficient method gives a clean scaling into the calculation of 
+Offensive Points. Some statistics, such as Points and Effective Field Goal Percentage, are equally 
+important, regardless of the position of a given player. Thus, these statistics have a constant coefficient that 
+does not change. Once all coefficients were applied to all statistics, the sum was taken to give Offensive 
+Points. The exact same method was applied to the Defensive Points calculation, but used the basic 
+defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls. As 
+turnovers and personal fouls are not desirable amongst players, the coefficients for these statistics is 
+negative, which allows for a scale of not only the good a player does, but also what they do poorly. This 
+coefficient method is similar to the Positional Adjustment metric applied in WAR calculation, which seeks to 
+adjust a player's importance based on what is expected of their position.
 
-The next step was creating a Team Adjustment statistic.
-As stated before, the PAR metric seeks to anticipate how valuable a player is to their given team, rather than as an average of the entire league.
-This gives more of an insight of how a team will fare without
-a certain player.
-We expect this statistic to change if a player were to switch teams.
-This is similar to the League Adjustment in WAR calculation, where a player's value is adjusted based on whether he plays in the American League or the National League.
-The
-Eastern and Western Conferences in the NBA have much less disparity compared to the MLB, and each conference plays each other much more frequently, so we instead change this to adjust a player's value to his specific team.
-The team assigned to a given
-player was the team where he played the most games during the 2020-2021 season.
-If a player had played an even amount of games for 2 separate teams, the team the player had played the most minutes for was assigned as his team.
-The Team Adjustment
-statistic is then calculated by taking the total minutes a player was on the court during the entire season, and diving it by a constant of 3,456 (the maximum number of minutes a player could have played during the shortened season, 48 minutes per game
-multiplied by 72 games).
-Then, the percentage of points a player scored for his team (player's total points divided by team's total points throughout the season) was calculated, and the two results were multiplied together.
-As a player cannot play 100 percent of
-his team's minutes, or score 100 percent of his team's points, the result is a number between 0 and 1.
-A similar adjustment is also used in the calculation of Box Plus Minus, which is a key factor in calculating Value Over Replacement Player, two of the advanced
-metrics PAR will be compared against.
-The goal of this adjustment is to give less of a penalty to players who play a majority of their team's minutes, and score a majority of their team's points.
-This helps truly elite players stand out amongst the pack, as well as
-players who may not be the best of the best, but matter more to their team specifically than in the grand scheme of things.
+The next step was creating a Team Adjustment statistic. As stated before, the PAR metric seeks to 
+anticipate how valuable a player is to their given team, rather than as an average of the entire league. This 
+gives more of an insight of how a team will fare without a certain player. We expect this statistic to change if 
+a player were to switch teams. This is similar to the League Adjustment in WAR calculation, where a 
+player's value is adjusted based on whether he plays in the American League or the National League. The 
+Eastern and Western Conferences in the NBA have much less disparity compared to the MLB, and each 
+conference plays each other much more frequently, so we instead change this to adjust a player's value to 
+his specific team. The team assigned to a given player was the team where he played the most games 
+during the 2020-2021 season. If a player had played an even amount of games for 2 separate teams, the 
+team the player had played the most minutes for was assigned as his team. The Team Adjustment statistic 
+is then calculated by taking the total minutes a player was on the court during the entire season, and diving 
+it by a constant of 3,456 (the maximum number of minutes a player could have played during the shortened 
+season, 48 minutes per game multiplied by 72 games). Then, the percentage of points a player scored for 
+his team (player's total points divided by team's total points throughout the season) was calculated, and the 
+two results were multiplied together. As a player cannot play 100 percent of his team's minutes, or score 
+100 percent of his team's points, the result is a number between 0 and 1. A similar adjustment is also used 
+in the calculation of Box Plus Minus, which is a key factor in calculating Value Over Replacement Player, 
+two of the advanced metrics PAR will be compared against. The goal of this adjustment is to give less of a 
+penalty to players who play a majority of their team's minutes, and score a majority of their team's points. 
+This helps truly elite players stand out amongst the pack, as well as players who may not be the best of the 
+best, but matter more to their team specifically than in the grand scheme of things.
 
-Lastly, WAR implements a Runs Per Win statistic, which gives a basic idea of how many runs are needed for a win in the MLB.
-Similarly, a Points Per Win statistic is created for the NBA, which allows a scaling down of the PAR statistic.
-We calculate this via the
-combined Offensive and Defensive Points statistic for a player divided by the number of minutes he played, then adding 2,160 (72 games per season times 30 teams in the NBA, thus, the total number of chances to win throughout the season).
-This gives a basic
-metric of a players points created as a function of how many minutes he played, and allows us to even the metric out a bit more from star players to role players.
-This statistic serves as the denominator of our PAR calculation.
+Lastly, WAR implements a Runs Per Win statistic, which gives a basic idea of how many runs are needed 
+for a win in the MLB. Similarly, a Points Per Win statistic is created for the NBA, which allows a scaling 
+down of the PAR statistic. We calculate this via the combined Offensive and Defensive Points statistic for a 
+player divided by the number of minutes he played, then adding 2,160 (72 games per season times 30 
+teams in the NBA, thus, the total number of chances to win throughout the season). This gives a basic 
+metric of a players points created as a function of how many minutes he played, and allows us to even the 
+metric out a bit more from star players to role players. This statistic serves as the denominator of our PAR 
+calculation.
 
@@
 
-This gives a good idea of how many points a player accounts for during a game, how important that is for his given team, and how important it is compared to all other players.
-The last step is to standardize this PAR statistic, so that the mean is 0, and the
-standard deviation is 1.
-Logically, this helps the idea of the metric in the sense that a perfectly league average player should have a PAR of 0, and his presence or absence from his team neither adds nor subtracts value.
-Thus, we have created a new NBA player
-metric, Points Above Replacement, PAR.
+This gives a good idea of how many points a player accounts for during a game, how important that is for 
+his given team, and how important it is compared to all other players. The last step is to standardize this 
+PAR statistic, so that the mean is 0, and the standard deviation is 1. Logically, this helps the idea of the 
+metric in the sense that a perfectly league average player should have a PAR of 0, and his presence or 
+absence from his team neither adds nor subtracts value. Thus, we have created a new NBA player metric, 
+Points Above Replacement, PAR.
 
@@
 First, the top 10 players in terms of PAR in the league will be analyzed. Then, the top 10 PAR values at each position will be evaluated.
-\begin{NBAtable}[tbp]
-  \caption{PAR Values from the Entire NBA)
+
+\begin{table}[tbp]
+  \caption{PAR Values from the Entire NBA}
   \label{tab:NBAtable}
@@
 \end{tabular}
-\end{NBAtable}
+\end{table}
 
-As can be seen, one player rises above all others in both PAR and VORP.
-That player is Nikola Jokic of the Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP season was.
-Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was doing it from the center position.
-Having a center that has the ability to perform in all aspects of the game, even those that his position does not require, proves his value to his team, which is why his value is so much higher in both the new PAR metric, and the accepted VORP metric.
-This logic applies to Nikola Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well.
-While they might not be considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, that can do anything on the court, and thus they are rewarded with a high PAR value.
-This makes sense, as without these players, a lot of the statistics their team accumulates are gone, so while they may not have as much value in the grand scheme of the NBA, they were very much the most valuable players for their teams.
-Another key thing to note is that some players, such as LeBron James, have a lower PAR than expected, and this could be due to the fact that they played most frequently in a position that did not match their skill set.
-LeBron James played primarily as a point guard, but his skillset matches that of a small forward or power forward.
-Thus, his strengths are not adequately measured, as he is essentially being played "out of position".
-\begin{PGtable}[tbp]
+As can be seen, one player rises above all others in both PAR and VORP. That player is Nikola Jokic of the 
+Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP 
+season was. Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was 
+doing it from the center position. Having a center that has the ability to perform in all aspects of the game, 
+even those that his position does not require, proves his value to his team, which is why his value is so 
+much higher in both the new PAR metric, and the accepted VORP metric. This logic applies to Nikola 
+Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well. While they might not be 
+considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, 
+that can do anything on the court, and thus they are rewarded with a high PAR value. This makes sense, as 
+without these players, a lot of the statistics their team accumulates are gone, so while they may not have as 
+much value in the grand scheme of the NBA, they were very much the most valuable players for their 
+teams. Another key thing to note is that some players, such as LeBron James, have a lower PAR than 
+expected, and this could be due to the fact that they played most frequently in a position that did not match 
+their skill set. LeBron James played primarily as a point guard, but his skillset matches that of a small 
+forward or power forward. Thus, his strengths are not adequately measured, as he is essentially being 
+played "out of position".
 
-  \caption{PAR Values from all Point Guards)
+\begin{table}[tbp]
+  \caption{PAR Values from all Point Guards}
   \label{tab:PGtable}
@@
 \end{tabular}
-\end{PGtable}
+\end{table}
 
-\begin{SGtable}[tbp]
-  \caption{PAR Values from all Shooting Guards)
+\begin{table}[tbp]
+  \caption{PAR Values from all Shooting Guards}
   \label{tab:SGtable}
@@
 \end{tabular}
-\end{SGtable}
+\end{table}
 
-\begin{SFtable}[tbp]
-  \caption{PAR Values from all Small Forwards)
+\begin{table}[tbp]
+  \caption{PAR Values from all Small Forwards}
   \label{tab:SFtable}
@@
 \end{tabular}
-\end{SFtable}
+\end{table}
 
-\begin{PFtable}[tbp]
-  \caption{PAR Values from all Power Forwards)
+\begin{table}[tbp]
+  \caption{PAR Values from all Power Forwards}
   \label{tab:PFtable}
@@
 \end{tabular}
-\end{PFtable}
+\end{table}
 
-\begin{Ctable}[tbp]
-  \caption{PAR Values from all Centers)
+\begin{table}[tbp]
+  \caption{PAR Values from all Centers}
   \label{tab:Ctable}
@@
 \end{tabular}
-\end{Ctable}
+\end{table}
 
-PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the multiple regression on PAR.
-These include Player Efficiency Rating, Win Shares, Box Plus Minus, and Value Over Replacement Player
+PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the 
+multiple regression on PAR. These include Player Efficiency Rating, Win Shares, Box Plus Minus, and 
+Value Over Replacement Player
 %PAR vs. PER
@@
 % Talk about drawbacks, what could be improved, etc.
-Ultimately, the goal of this statistic is to allow a reader to gague a player's value to his team based on a league average player.
-As previously stated, the metric is adjusted so that a league average player has a PAR value of 0.
-Based on all other players' PAR values, we can create a sort of "legend", a rough guideline for what a player's role will be based on the threshold his PAR value falls under.
+% Talk about how it is in agreement with existing measures
+Ultimately, the goal of this statistic is to allow a reader to gauge a player's value to his team based on a 
+league average player. As previously stated, the metric is adjusted so that a league average player has a 
+PAR value of 0. Based on all other players' PAR values, we can create a sort of "legend", a rough guideline 
+for what a player's role will be based on the threshold his PAR value falls under.
 
 \bibliographystyle{chicago}
-%\bibliography{citations.bib}
-% \section*{acknowledgements}
+\bibliography{citations.bib}
+\section*{Acknowledgements}
 The authors thank the University of Connecticut and the UConn Department of Statistics.
@@
 % If there is more than one student author, you must move the comment below.
-\section*{about the student author}
+\section*{About the Student Author}
 Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.
@@
 % The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
-\section*{press summary}
+\section*{Press Summary}
 

### 2022-04-04 Manuscript/Manuscript.tex
Add files via upload

@@
 
+\usepackage{float}
 \usepackage{xr-hyper}
@@
 \usepackage{xr}
-%\externaldocument{isgee}
-%\externaldocument{supp}
 
@@
 }
+
 \begin{document}
 
+\begin{titlepage}
+   \begin{center}
+       \vspace*{1cm}
+       \Huge
+       \textbf{Points Above Replacement}
+
+       \Large
+       \vspace{0.5cm}
+        A New NBA Metric to Evaluate Player Performance
+
+       \vspace{1.5cm}
+
+       \textbf{Brian Krikorian}
+
+       \vfill
+
+       \includegraphics[width=0.4\textwidth]{UCONNwordmark}
+
+       \vfill
+
+       Mentor: Jun Yan\\
+       Data Science
+
+       \vspace{0.8cm}
+
+       \includegraphics[width=0.4\textwidth]{UCONNoakleaf}
+
+        \Large    
+       Department of Statistics\\
+       University of Connecticut\\
+       Storrs, CT\\
+
+   \end{center}
+\end{titlepage}
 % Abstracts are required.
@@
 % Should dive more in depth about how everything was obtained, calculated, etc.
+
 The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but 
@@
 coefficient method is similar to the Positional Adjustment metric applied in WAR calculation, which seeks to 
-adjust a player's importance based on what is expected of their position.
+adjust a player's importance based on what is expected of their position. The coefficients for each position are listed below.
+
+\vfill
+\begin{table}[H]
+  \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
+  \label{tab:Coefficientstable}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Statistic & Point Guard & Shooting Guard & Small Forward & Power Forward & Center\\
+  \midrule
+ Effective FG Percentage & 200 & 200 & 200 & 200 & 200\\
+ \midrule
+ 3 Point Percentage & 300 & 275 & 250 & 225 & 200\\
+ \midrule
+ Free Throw Percentage & 100 & 90 & 80 & 70 & 60\\
+ \midrule
+ Offensive Rebounds & 1 & 1.5 & 2 & 2.5 & 3\\
+ \midrule
+ Assists & 4 & 3.5 & 3 & 2.5 & 2\\
+ \midrule
+ Points & 2 & 2 & 2 & 2 & 2\\
+ \midrule
+ Turnovers & -5 & -4.5 & -4 & -3.5 & -3\\
+ \midrule
+ Defensive Rebounds & 2 & 2.5 & 3 & 3.5 & 4\\
+ \midrule
+ Total Rebounds & 3 & 3.25 & 3.5 & 3.75 & 4\\
+ \midrule
+ Steals & 5 & 4.5 & 4 & 3.5 & 3\\
+ \midrule
+ Blocks & 3 & 3.5 & 4 & 4.5 & 5\\
+ \midrule
+ Personal Fouls & -3 & -3 & -3 & -3 & -3\\
+  \bottomrule
+\end{tabular}
+\end{table}
 
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from the Entire NBA}
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from all Point Guards}
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from all Shooting Guards}
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from all Small Forwards}
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from all Power Forwards}
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Values from all Centers}
@@
 Value Over Replacement Player
-%PAR vs. PER
-%PAR vs. WS
-%PAR vs. BPM
-%PAR vs. VORP
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.6]{PERvsPAR}
+  \caption{Player Efficiency Ratings (x) vs. Points Above Replacement (y)}
+  \label{fig:Fig1}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.6]{WSvsPAR}
+  \caption{Win Shares (x) vs. Points Above Replacement (y)}
+  \label{fig:Fig2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.6]{BPMvsPAR}
+  \caption{Box Plus Minus (x) vs. Points Above Replacement (y)}
+  \label{fig:Fig3}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.6]{VORPvsPAR}
+  \caption{Value Over Replacement Player (x) vs. Points Above Replacement (y)}
+  \label{fig:Fig4}
+\end{figure}
+
+It can be seen that the graphs of PAR and Win Shares, as well as PAR and Value Over Replacement Player 
+fit nicely, with a relatively positive and linear correlation. However, the graphs of PAR and Box Plus Minus, 
+as well as PAR and Player Efficiency Rating appear to have less of a linear distribution. This can be 
+attributed to the scaling methods of each statistic. Since Win Shares and Value Over Replacement Player 
+follow a similar scale, with a minimum slightly below 0, and a maximum somewhere in the range of 10, the 
+scales match, and each player's value of each metric fits similarly enough to form a linear distribution. 
+However, Box Plus Minus ranges from -40 to above 20, so we see the graph centered around 0, where the 
+majority of players fall, and going almost straight upwards based on their PAR value. Player Efficiency 
+Rating has a similar scale, so a similar effect is shown. In order to see how Points Above Replacement fits 
+in terms of all of these accepted metrics, a multiple regression will be run, with the 4 accepted metrics as 
+regressors, and with PAR as the independent variable.
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale = 0.6]{MultipleRegression}
+  \caption{Multiple Regression with Regressors PER, WS, BPM, and VORP and Independent Variable PAR}
+  \label{fig:Fig5}
+\end{figure}
+
+The key statistic here is the adjusted R-squared value of 0.6974. This shows that 69.74 percent of variation 
+in PAR can be explained by these other 4 accepted metrics. This shows a clear correlation between PAR 
+and the metrics, but also shows that PAR has something unique to offer.
 
@@
 for what a player's role will be based on the threshold his PAR value falls under.
+
+\begin{table}[H]
+  \caption{PAR Legend}
+  \label{tab:PARLegend}
+\centering
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Role &  PAR\\
+  \midrule
+Benchwarmer & Less than -0.43\\
+  \midrule
+Role Player & -0.43 to 0.08\\
+  \midrule
+Starter & 0.08 to 1.09\\
+  \midrule
+All-Star & 1.09 to 1.94\\
+ \midrule
+Superstar & Greater than 1.94\\
+  \bottomrule
+\end{tabular}
+\end{table}
+
+This legend was calculated based on a quantile calculation of all PAR data. It is not an even distribution, as 
+it is assumed that there are many more benchwarmers in the NBA than there are superstars. Thus, 
+benchwarmers are defined as the bottom 50 percent of the league, as an NBA roster of about 15 players 
+will only give 7 or 8 players significant minutes. Players between the 50th and 75th percentile are defined 
+as role players, as they get significant minutes, but do not make an impact enough to be considered a solid 
+starter. This is where  a "league average" player is expected to fall, as 0 is contained in this part of the 
+legend, and 0 represents a league average player via this metric. Next, the 75th to 90th percentile are 
+defined as starters, because only 5 players can start a game, and, more often than not, a team only has 3 
+or 4 players who are guaranteed starters. 90th to 95th percentiles represent all-stars, as that is clearly a 
+very prestigious area to be a part of. Lastly, it is assumed that only the top 5 percent of players in the 
+league can be deemed "superstars", so they comprise the 95th to 100th percentile of the NBA. By this 
+method, it is felt that a more realistic legend for PAR has been created as opposed to just breaking up the 
+data evenly into 5 groups.
 

### 2022-04-05 Manuscript/Manuscript.tex
somm comments

@@
-\documentclass[12pt]{article}
+\documentclass[12pt, titlepage]{article}
 \usepackage[margin=1in]{geometry}
@@
 \captionsetup{labelformat=simple, labelsep=period}
-\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
-\renewcommand{\theequation}{\arabic{equation}}
+% \newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
+% \renewcommand{\theequation}{\arabic{equation}}
 \makeatletter
@@
   }{\end{quoting}}
+
 \title{Points Above Replacement: A New NBA Metric to Evaluate Player Performance}
@@
  \end{titlepage}
+
 % Abstracts are required.
+
+\jy{watch linewidth in source; keep it under 80}
+
 \section*{Abstract}
@@
 
-\vfill
-\begin{table}[H]
+\jy{no hard coded spacing like vfill}
+
+\jy{no horizontal lines in tables; float with tbp}
+
+\begin{table}[tbp]
   \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
@@
 
+Table~\ref{tab:Coefficientstable} summarizes ...
+
 The next step was creating a Team Adjustment statistic. As stated before, the PAR metric seeks to 
@@
 
-Once all supporting statistics of PAR have been created, all that is left to do is combine them to achieve our PAR values for each player in the NBA. The formula for PAR is as follows:
-
+Once all supporting statistics of PAR have been created, all that is left to do is combine them to achieve our PAR values for each player in the NBA. The formula for PAR is
 \begin{equation}
-((Offensive Points + DefensivePoints) * (Team Adjustment))/(Points Per Win)
+  \label{eq:par}
+  \frac{(\text{Offensive Points} + \text{Defensive Points}) \times \text{Team Adjustment}}
+  {\text{Points Per Win}}.
 \end{equation}
-
 This gives a good idea of how many points a player accounts for during a game, how important that is for 

### 2022-04-14 Manuscript/Manuscript.tex
Add files via upload

--- 2022-04-04 Manuscript/Manuscript.tex
@@
 \captionsetup{labelformat=simple, labelsep=period}
-\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
-\renewcommand{\theequation}{\arabic{equation}}
-\makeatletter
-\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
+%\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
+%\renewcommand{\theequation}{\arabic{equation}}
+%\makeatletter
+%\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
 \makeatother
@@
 \section*{Abstract}
-In attempting to predict the score of an NBA game, players who are injured, suspended, or for any other 
-reason not playing have a significant impact on said prediction. Baseball uses a statistic called Wins Above 
-Replacement, or WAR, to tell how many wins a team would gain or lose if they replaced a certain player 
-with one who is league average. The goal of this paper is to create a similar statistic, called Points Above 
-Replacement, or PAR, that uses statistics from throughout the season to predict how many points a team 
-gains or loses by missing a certain player, and thus having to replace him with one who is "league 
-average". The statistic is standardized and adjusted by both position and value to a player's given team. 
-The model roughly follows the calculation of WAR in baseball, assigning values to points created on offense 
-and defense, as well as a positional and team adjustment. A comparison with the created metric along with 
-other well-known advanced player metrics is done via a multiple regression.
+In attempting to predict the score of an NBA game, players who are 
+injured, suspended, or for any other 
+reason not playing have a significant impact on said prediction. Baseball 
+uses a statistic called Wins Above 
+Replacement, or WAR, to tell how many wins a team would gain or lose if 
+they replaced a certain player 
+with one who is league average. The goal of this paper is to create a 
+similar statistic, called Points Above 
+Replacement, or PAR, that uses statistics from throughout the season to 
+predict how many points a team 
+gains or loses by missing a certain player, and thus having to replace him 
+with one who is "league 
+average". The statistic is standardized and adjusted by both position and 
+value to a player's given team. 
+The model roughly follows the calculation of WAR in baseball, assigning 
+values to points created on offense 
+and defense, as well as a positional and team adjustment. A comparison 
+with the created metric along with 
+other well-known advanced player metrics is done via a multiple 
+regression.
 
@@
 \section*{Keywords} 
-NBA; Basketball; Player Performance; Basketball Metrics;
+Analytics; Basketball; Player Value; Sports Data; Statistics; 
 \vspace{.12 in}
@@
 %Why is this important/interesting? What has been done before on this topic? (Literature Review) What am I introducing that is new? 
-There exists many prediction models for NBA basketball, many with the purpose of anticipating the final 
-score of a given game. However, the majority of these models use team average statistics to base their 
-decision, similar to the openWAR method in baseball introduced by Greg Matthews and others. However, 
-teams rosters can change every night, and do often. When star players are ruled out, players of lower 
-quality take their minutes, and are expected to perform at a lower level. When lower level players do not 
-play in a given game, star players are expected to play more minutes, which most likely will cause a slight 
-uptick in performance. This reasoning is the cause for the creation of the new metric, PAR. The measure of 
-how many points a team will gain or lose if a certain player does not play. The metric is created based on 
-the last completed season, the 2020-2021 season, which was cut to 72 games, as opposed to 82, due to 
-the COVID-19 pandemic. Future models could be adjusted to a full 82 game season, and automated to 
-update statistics as the season goes on. Position and team adjustments allow for a player's value to his 
-specific team to be measured, giving a better expectation for their presence or absence. Adjusting to a 
-position allows one to analyze a player based on what his position requires. A point guard is expected to 
-pass, shoot three pointers, and get steals more than he is expected to block shots and rebound. The 
-opposite is true for centers, so different coefficients are created based on the primary position a player 
-played throughout the season. The team adjustment is a function of how many minutes a player played 
-throughout the entire season, and how many of their team's total points were scored by them. If a player 
-plays a majority of his team's minutes, and scores a relatively high percentage of his team's points, he will 
-be more valuable to his team, and his team will be hurt more by his absence in a game.
+There exists many prediction models for NBA basketball, many with the 
+purpose of anticipating the final 
+score of a given game. However, the majority of these models use team 
+average statistics to base their 
+decisions. However, 
+teams rosters can change every night, and do often. When star players 
+are ruled out, players of lower 
+quality take their minutes, and are expected to perform at a lower level. 
+When lower level players do not 
+play in a given game, star players are expected to play more minutes, 
+which most likely will cause a slight 
+uptick in performance. This reasoning is the cause for the creation of the 
+new metric, PAR. PAR is based on the WAR statistic in baseball, which 
+seeks to show player value based on average level. Many changes are 
+constantly made to the statistic, however, and it is very subjective. 
+\citet{Baumer} talks about how openWAR was concerned with issues of 
+how WAR was previously calculated, such as accounting for uncertainty 
+and reproductivity. Similarly, the measure of PAR seeks to add on to 
+existing metrics by accounting for importance to a team, importance by 
+position, and adjusting for amount of playing time. Points Above 
+Replacement is a measure of how many points a team will gain or lose if 
+a certain player does not play. 
+The metric is created based on the last completed season, the 2020-2021 
+season, which was cut to 72 games, as opposed to 82, due to 
+the COVID-19 pandemic.
+
+This idea of Points Above Replacement is prefaced by many different 
+statistical analyses that have been done over the years. \citet{Dehesa} 
+discusses the different factors that influence player performance, and 
+identifies different players' profiles in order to better analyze their 
+contributions to their team. Similarly, PAR is mainly concerned with a 
+player's value to the team they are currently on, rather than a function of 
+the entire NBA, so that individual games can be predicted more 
+accurately, and also so that individual teams can analyze the value of 
+their roster, which is similar to the goal of the cited paper, and a part of 
+where the influence was drawn.
+
+\citet{Fearnhead} also tries to find a way to estimate NBA player ability. 
+The analysis is based on splitting player value into offensive and 
+defensive categories, then combining the two to get a total value. WAR is 
+calculated very similarly, in that it assigns a value to all aspects of 
+baseball, and then combines them \citep{BaseballWAR}. PAR also 
+assumes this method to create the metric, which will be discussed later. 
+Another aspect of this analysis that PAR takes on is centering the data, so 
+that the league average is 0, and all other data can be based around that. 
+A key difference is that while this paper does break up the analysis by 
+position, it only recognizes 3 different positions, while PAR looks at all 5 
+individual positions in the NBA.
+
+No similar papers where a new NBA statistic to analyze individual points 
+that a player adds to his team were found, but pieces of other NBA 
+analytics were very influential in the creation of PAR. Similar to how 
+openWAR sought to fix the typical WAR statistic, PAR seeks to stand out 
+from other accepted advanced metrics, such as BPM and PER. 
+\citet{Hamalian} talks about the flaws that exist in PER, such as the lack 
+of centering in the data, making the league average actually vary per 
+season. The cited article also talks about how the pace statistic in PER 
+ultimately does not do anything. Thus, PAR takes many of the same 
+box-score 
+statistics that PAR does, but seeks to center its data to form a 
+season-by-season league average, and attributes a player's value to his 
+team's total points and total minutes, rather than accounting for the pace 
+of the team. There are similarities with PER that this article still believes 
+are not efficient, and those shortcomings will be discussed further in later 
+sections.
+
+One of the main adjustments in PAR that occurs is that of a positional 
+adjustment. Different positions have different requirements, so box score 
+statistics need more analysis than meets the eye to really show a player's 
+value. \citet{Piette} makes a point of this in the analysis of field goal 
+percentage based on distance from the basket. Adjusting by positional 
+need is a key aspect of PAR that was inspired by the metrics in the cited 
+paper. Players in the NBA all have different skillsets, and different 
+positions call for these specific skillsets in order for a team to be 
+successful as a unit, which is a key point in the cited paper, as well as in 
+PAR.
+
+As previously stated, there were no other papers found in which a new 
+NBA metric was attempted to be created, so the question is that of what 
+PAR can add to previously accepted statistics.
+Position and team adjustments 
+allow for a player's value to his 
+specific team to be measured, giving a better expectation for their 
+presence or absence. This is similar to how WAR is calculated, which 
+takes into account a positional and league adjustment 
+\citep{BaseballWAR}. Adjusting to a 
+position allows one to analyze a player based on what his position 
+requires. The team adjustment is a function of how 
+many minutes a player played 
+throughout the entire season, and how many of their team's total points 
+were scored by them. If a player 
+plays a majority of his team's minutes, and scores a relatively high 
+percentage of his team's points, he will 
+be more valuable to his team, and his team will be hurt more by his 
+absence in a game. The idea of how much an individual team will value 
+an individual player is the key unique factor in PAR that causes it to stand 
+out.
 
@@
 % Include basic graphics here?
-All basic and advanced statistics from the 2020-2021 season were collected from the Basketball Reference 
-website. Each teams total points throughout the course of the season were also collected from the 
-Basketball Reference website. From the basic statistics, 4 metrics were created in order to calculate PAR. 
-Offensive Points is a function of how many points a player will create on offense. While the coefficients vary 
-by position, the statistics used are effective field goal percentage, three point percentage, free throw 
-percentage, offensive rebounds, assists, points, and turnovers. Similarly, Defensive Points is a function of 
-how many points a player helps prevent while his team is on defense. The coefficients also vary by position, 
-but this metric is based on defensive rebounds, total rebounds, steals, blocks, and personal fouls. The 
-Positional Adjustment metric creates a coefficient of how valuable a player is to their individual team, and is 
-based on how many minutes a player plays relative to their team, as well as how many points they score 
-relative to their teams total points. The last statistic created is Points Per Win, which is based on the 
-average amount of points a player will create in a game. This function is based on the sum of Offensive and 
-Defensive Points, and is scaled to incorporate the total number of games, minutes, and players in a season. 
-This statistic is very similarly calculated to Runs Per Win in the WAR statistic. Given that over the course of 
-a 72 game season, all teams will play each other at least once, we assume a relatively equal distribution in 
-terms of strength of schedule. Advanced statistics for each player were also collected in order to perform a 
-regression, to see how PAR compares with known and accepted metrics. Value Over Replacement Player, 
-also known as VORP, was one of the metrics used, and is calculated with the help of Box Score Plus 
-Minus, also known as BPM. These statistics also help give a relative estimate of a player's value compared 
-to that of an average player, but they translate the statistic to a league average team as well. PAR does not 
-do this, because it is concerned with how valuable a player is to his specific team, not throughout the entire 
-league. If a player switched teams, his PAR value would most likely change, as his importance to one team 
-may be more or less than it would to another. For simplicity, the team that a player played his most games 
-on was taken into consideration for this metric. Other statistics used include Player Efficiency Rating, a 
-per-minute 
-rating of player performance, and Win Shares, which estimates the number of wins a player creates 
-for his team throughout the season. Due to all of these metrics' relative similarity to PAR, it is suggested 
-that if they are highly correlated with PAR, it is a successful metric. However, we expect some differentiation 
-between the metrics, as they all vary slightly in what they attempt to convey. The relative correlation 
-between all these statistics shows that PAR is related to other advanced metrics analyzing player efficiency, 
+All basic and advanced statistics from the 2020-2021 season were 
+collected from the Basketball Reference 
+website, as well as each team's total points throughout the course of the season \citep{BasketballReference}. From the basic statistics, 4 metrics were 
+created in order to calculate PAR. 
+Offensive Points is a function of how many points a player will create on 
+offense. While the coefficients vary 
+by position, the statistics used are effective field goal percentage, three 
+point percentage, free throw 
+percentage, offensive rebounds, assists, points, and turnovers. Similarly, 
+Defensive Points is a function of how many points a player helps prevent 
+while his team is on defense. The coefficients also vary by position, 
+but this metric is based on defensive rebounds, total rebounds, steals, 
+blocks, and personal fouls.
+
+The Positional Adjustment metric creates a coefficient of how valuable a 
+player is to their individual team, and is 
+based on how many minutes a player plays relative to their team, as well 
+as how many points they score 
+relative to their teams total points. The last statistic created is Points Per 
+Win, which is based on the 
+average amount of points a player will create in a game. This function is 
+based on the sum of Offensive and 
+Defensive Points, and is scaled to incorporate the total number of games, 
+minutes, and players in a season. 
+This statistic is very similarly calculated to Runs Per Win in the WAR 
+statistic. Given that over the course of 
+a 72 game season, all teams will play each other at least once, we 
+assume a relatively equal distribution in 
+terms of strength of schedule.
+
+Advanced statistics for each player were also collected in order to perform 
+a 
+regression, to see how PAR compares with known and accepted metrics. 
+Value Over Replacement Player, 
+also known as VORP, was one of the metrics used, and is calculated with 
+the help of Box Score Plus 
+Minus, also known as BPM. These statistics also help give a relative 
+estimate of a player's value compared 
+to that of an average player, but they translate the statistic to a league 
+average team as well. PAR does not 
+do this, because it is concerned with how valuable a player is to his 
+specific team, not throughout the entire 
+league. If a player switched teams, his PAR value would most likely 
+change, as his importance to one team 
+may be more or less than it would to another. For simplicity, the team that 
+a player played his most games 
+on was taken into consideration for this metric.
+
+Similarities to BPM, and therefore VORP, can be explained by many 
+different factors. BPM centers data so that the league average is 0, and 
+creates coefficients for factors based on a player's position and offensive 
+role. While PAR is not concerned with offensive role, it does take into 
+account position, and assumes that position, for the most part, is 
+correlated with offensive role. Intentional usage of only universally 
+available statistics allow for easy calculation as well as easy 
+understanding for audiences. The key difference is that of playing time not 
+being a factor in BPM and VORP, which is obviously a key factor in PAR 
+\citep{BasketballReferenceBPM}.
+
+Other statistics used include Player Efficiency Rating, a 
+per-minute rating of player performance, and Win Shares, which 
+estimates the number of wins a player creates 
+for his team throughout the season. Due to all of these metrics' relative 
+similarity to PAR, it is suggested 
+that if they are highly correlated with PAR, it is a successful metric. 
+However, we expect some differentiation 
+between the metrics, as they all vary slightly in what they attempt to 
+convey. The relative correlation 
+between all these statistics shows that PAR is related to other advanced 
+metrics analyzing player efficiency, 
 but also that it introduces something new in basketball statistics.
@@
 
-The basic method for calculating the PAR method was based on how WAR is calculated in baseball, but 
-also took influences from other advanced basketball statistics. WAR is based on Offensive and Defensive 
-Runs, which are calculated subjectively via attributes of the game such as hitting, base running, fielding, 
-and so forth. The subjectivity is in the coefficients chosen to scale statistics which impact Offensive and 
-Defensive Runs. Thus, there are actually an infinite different kinds of WAR in baseball, depending on which 
-method of calculating Offensive and Defensive Runs is used. Similarly, PAR is created by calculating 
-Offensive and Defensive Points statistics, to analyze how many points a player adds for his team, and how 
-many he prevents the other team from scoring. Using the basic offensive statistics of Effective Field Goal 
-Percentage, Three Point Percentage, Free Throw Percentage, Offensive Rebounds, Assists, Points, and 
-Turnovers, we assign a coefficient to them based on how important they are for a given position. Point 
-guards are expected to pass more than centers, and a point guard's passing ability has more value to his 
-team than a center, so more weight is placed on that statistic for point guards. This goes for all positions, 
-and a coefficient matrix of a constant scale is created. That is to say, assists have a coefficient from point 
-guards, shooting guards, small forwards, power forwards, and centers, respectively, of 4, 3.5, 3, 2.5, and 2. 
-The coefficient by position method is one similar to that of Box Plus Minus, another advanced NBA metric. 
-The position a player was assigned for the calculation was the position where he played the most minutes 
-throughout the 2020-2021 season. This coefficient method gives a clean scaling into the calculation of 
-Offensive Points. Some statistics, such as Points and Effective Field Goal Percentage, are equally 
-important, regardless of the position of a given player. Thus, these statistics have a constant coefficient that 
-does not change. Once all coefficients were applied to all statistics, the sum was taken to give Offensive 
-Points. The exact same method was applied to the Defensive Points calculation, but used the basic 
-defensive statistics of Defensive Rebounds, Total Rebounds, Steals, Blocks, and Personal Fouls. As 
-turnovers and personal fouls are not desirable amongst players, the coefficients for these statistics is 
-negative, which allows for a scale of not only the good a player does, but also what they do poorly. This 
-coefficient method is similar to the Positional Adjustment metric applied in WAR calculation, which seeks to 
-adjust a player's importance based on what is expected of their position. The coefficients for each position are listed below.
+The basic method for calculating the PAR method was based on how 
+WAR is calculated in baseball, but 
+also took influences from other advanced basketball statistics. WAR is 
+based on Offensive and Defensive 
+Runs, which are calculated subjectively via attributes of the game such as 
+hitting, base running, fielding, 
+and so forth. The subjectivity is in the coefficients chosen to scale 
+statistics which impact Offensive and 
+Defensive Runs. Thus, there are actually an infinite different kinds of WAR 
+in baseball, depending on which 
+method of calculating Offensive and Defensive Runs is used. Similarly, 
+PAR is created by calculating 
+Offensive and Defensive Points statistics, to analyze how many points a 
+player adds for his team, and how 
+many he prevents the other team from scoring. Using the basic offensive 
+statistics of Effective Field Goal 
+Percentage, Three Point Percentage, Free Throw Percentage, Offensive 
+Rebounds, Assists, Points, and 
+Turnovers, we assign a coefficient to them based on how important they 
+are for a given position. Point 
+guards are expected to pass more than centers, and a point guard's 
+passing ability has more value to his 
+team than a center, so more weight is placed on that statistic for point 
+guards. This goes for all positions, 
+and a coefficient matrix of a constant scale is created. That is to say, 
+assists have a coefficient from point 
+guards, shooting guards, small forwards, power forwards, and centers, 
+respectively, of 4, 3.5, 3, 2.5, and 2. 
+The coefficient by position method is one similar to that of Box Plus 
+Minus, another advanced NBA metric. 
+The position a player was assigned for the calculation was the position 
+where he played the most minutes 
+throughout the 2020-2021 season. This coefficient method gives a clean 
+scaling into the calculation of 
+Offensive Points. Some statistics, such as Points and Effective Field Goal 
+Percentage, are equally 
+important, regardless of the position of a given player. Thus, these 
+statistics have a constant coefficient that 
+does not change. Once all coefficients were applied to all statistics, the 
+sum was taken to give Offensive 
+Points. The exact same method was applied to the Defensive Points 
+calculation, but used the basic 
+defensive statistics of Defensive Rebounds, Total Rebounds, Steals, 
+Blocks, and Personal Fouls. As 
+turnovers and personal fouls are not desirable amongst players, the 
+coefficients for these statistics is 
+negative, which allows for a scale of not only the good a player does, but 
+also what they do poorly. This 
+coefficient method is similar to the Positional Adjustment metric applied in 
+WAR calculation, which seeks to 
+adjust a player's importance based on what is expected of their position. 
+The coefficients for each position are listed in table 
+\ref{tab:Coefficientstable}. Coefficients are subjective, but were changed 
+to have a constant scale by position, and create a PAR scale that lined up 
+closely with other advanced metrics.
 
-\vfill
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
@@
   \toprule
-  Statistic & Point Guard & Shooting Guard & Small Forward & Power Forward & Center\\
+  Statistic & Point & Shooting & Small & Power  & Center\\
+  & Guard & Guard & Forward & Forward & \\
   \midrule
  Effective FG Percentage & 200 & 200 & 200 & 200 & 200\\
- \midrule
  3 Point Percentage & 300 & 275 & 250 & 225 & 200\\
- \midrule
  Free Throw Percentage & 100 & 90 & 80 & 70 & 60\\
- \midrule
  Offensive Rebounds & 1 & 1.5 & 2 & 2.5 & 3\\
- \midrule
  Assists & 4 & 3.5 & 3 & 2.5 & 2\\
- \midrule
  Points & 2 & 2 & 2 & 2 & 2\\
- \midrule
  Turnovers & -5 & -4.5 & -4 & -3.5 & -3\\
- \midrule
  Defensive Rebounds & 2 & 2.5 & 3 & 3.5 & 4\\
- \midrule
  Total Rebounds & 3 & 3.25 & 3.5 & 3.75 & 4\\
- \midrule
  Steals & 5 & 4.5 & 4 & 3.5 & 3\\
- \midrule
  Blocks & 3 & 3.5 & 4 & 4.5 & 5\\
- \midrule
  Personal Fouls & -3 & -3 & -3 & -3 & -3\\
@@
 
-The next step was creating a Team Adjustment statistic. As stated before, the PAR metric seeks to 
-anticipate how valuable a player is to their given team, rather than as an average of the entire league. This 
-gives more of an insight of how a team will fare without a certain player. We expect this statistic to change if 
-a player were to switch teams. This is similar to the League Adjustment in WAR calculation, where a 
-player's value is adjusted based on whether he plays in the American League or the National League. The 
-Eastern and Western Conferences in the NBA have much less disparity compared to the MLB, and each 
-conference plays each other much more frequently, so we instead change this to adjust a player's value to 
-his specific team. The team assigned to a given player was the team where he played the most games 
-during the 2020-2021 season. If a player had played an even amount of games for 2 separate teams, the 
-team the player had played the most minutes for was assigned as his team. The Team Adjustment statistic 
-is then calculated by taking the total minutes a player was on the court during the entire season, and diving 
-it by a constant of 3,456 (the maximum number of minutes a player could have played during the shortened 
-season, 48 minutes per game multiplied by 72 games). Then, the percentage of points a player scored for 
-his team (player's total points divided by team's total points throughout the season) was calculated, and the 
-two results were multiplied together. As a player cannot play 100 percent of his team's minutes, or score 
-100 percent of his team's points, the result is a number between 0 and 1. A similar adjustment is also used 
-in the calculation of Box Plus Minus, which is a key factor in calculating Value Over Replacement Player, 
-two of the advanced metrics PAR will be compared against. The goal of this adjustment is to give less of a 
-penalty to players who play a majority of their team's minutes, and score a majority of their team's points. 
-This helps truly elite players stand out amongst the pack, as well as players who may not be the best of the 
-best, but matter more to their team specifically than in the grand scheme of things.
+The next step was creating a Team Adjustment statistic. As stated before, 
+the PAR metric seeks to 
+anticipate how valuable a player is to their given team, rather than as an 
+average of the entire league. This 
+gives more of an insight of how a team will fare without a certain player. 
+We expect this statistic to change if 
+a player were to switch teams. This is similar to the League Adjustment in 
+WAR calculation, where a 
+player's value is adjusted based on whether he plays in the American 
+League or the National League. The 
+Eastern and Western Conferences in the NBA have much less disparity 
+compared to the MLB, and each 
+conference plays each other much more frequently, so we instead change 
+this to adjust a player's value to 
+his specific team. The team assigned to a given player was the team 
+where he played the most games 
+during the 2020-2021 season. If a player had played an even amount of 
+games for 2 separate teams, the 
+team the player had played the most minutes for was assigned as his 
+team. The Team Adjustment statistic 
+is then calculated by taking the total minutes a player was on the court 
+during the entire season, and diving 
+it by a constant of 3,456 (the maximum number of minutes a player could 
+have played during the shortened 
+season, 48 minutes per game multiplied by 72 games). Then, the 
+percentage of points a player scored for 
+his team (player's total points divided by team's total points throughout the 
+season) was calculated, and the 
+two results were multiplied together. As a player cannot play 100 percent 
+of his team's minutes, or score 
+100 percent of his team's points, the result is a number between 0 and 1. 
+A similar adjustment is also used 
+in the calculation of Box Plus Minus, which is a key factor in calculating 
+Value Over Replacement Player, 
+two of the advanced metrics PAR will be compared against. The goal of 
+this adjustment is to give less of a 
+penalty to players who play a majority of their team's minutes, and score a 
+majority of their team's points. 
+This helps truly elite players stand out amongst the pack, as well as 
+players who may not be the best of the 
+best, but matter more to their team specifically than in the grand scheme 
+of things.
 
-Lastly, WAR implements a Runs Per Win statistic, which gives a basic idea of how many runs are needed 
-for a win in the MLB. Similarly, a Points Per Win statistic is created for the NBA, which allows a scaling 
-down of the PAR statistic. We calculate this via the combined Offensive and Defensive Points statistic for a 
-player divided by the number of minutes he played, then adding 2,160 (72 games per season times 30 
-teams in the NBA, thus, the total number of chances to win throughout the season). This gives a basic 
-metric of a players points created as a function of how many minutes he played, and allows us to even the 
-metric out a bit more from star players to role players. This statistic serves as the denominator of our PAR 
+Lastly, WAR implements a Runs Per Win statistic, which gives a basic 
+idea of how many runs are needed 
+for a win in the MLB. Similarly, a Points Per Win statistic is created for the 
+NBA, which allows a scaling 
+down of the PAR statistic. We calculate this via the combined Offensive 
+and Defensive Points statistic for a 
+player divided by the number of minutes he played, then adding 2,160 (72 
+games per season times 30 
+teams in the NBA, thus, the total number of chances to win throughout the 
+season). This gives a basic 
+metric of a players points created as a function of how many minutes he 
+played, and allows us to even the 
+metric out a bit more from star players to role players. This statistic serves 
+as the denominator of our PAR 
 calculation.
 
-Once all supporting statistics of PAR have been created, all that is left to do is combine them to achieve our PAR values for each player in the NBA. The formula for PAR is as follows:
+Once all supporting statistics of PAR have been created, all that is left to 
+do is combine them to achieve our PAR values for each player in the 
+NBA. The formula for PAR is listed below.
 
 \begin{equation}
-((Offensive Points + DefensivePoints) * (Team Adjustment))/(Points Per Win)
+ \label{eq:PAR}
+  \frac{(\text{Offensive Points} + \text{Defensive Points}) \times \text{Team Adjustment}}
+  {\text{Points Per Win}}.
 \end{equation}
 
-This gives a good idea of how many points a player accounts for during a game, how important that is for 
-his given team, and how important it is compared to all other players. The last step is to standardize this 
-PAR statistic, so that the mean is 0, and the standard deviation is 1. Logically, this helps the idea of the 
-metric in the sense that a perfectly league average player should have a PAR of 0, and his presence or 
-absence from his team neither adds nor subtracts value. Thus, we have created a new NBA player metric, 
-Points Above Replacement, PAR.
+\ref{eq:PAR} gives a good idea of how many points a player accounts for 
+during a 
+game, how important that is for 
+his given team, and how important it is compared to all other players. The 
+last step is to standardize this 
+PAR statistic, so that the mean is 0, and the standard deviation is 1. 
+Logically, this helps the idea of the 
+metric in the sense that a perfectly league average player should have a 
+PAR of 0, and his presence or 
+absence from his team neither adds nor subtracts value. Thus, we have 
+created a new NBA player metric, 
+Points Above Replacement, PAR. All of the calculations, multiple regression, and graphs were created using R \citep{R}.
 
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from the Entire NBA}
@@
  1 & Nikola Jokic & C & Denver Nuggets & 7.69\\
-  \midrule
  2 & Nikola Vucevic & C & Orlando Magic & 6.55\\
-  \midrule
  3 & Julius Randle & PF & New York Knicks & 6.49\\
-  \midrule
  4 & Luka Doncic & PG & Dallas Mavericks & 4.61\\
-  \midrule
  5 & Damian Lillard & PG & Portland Trail Blazers & 4.47\\
-  \midrule
  6 & Giannis Antetokounmpo & PF & Milwaukee Bucks & 4.21\\
-  \midrule
  7 & Stephen Curry & PG & Golden State Warriors & 4.17\\
-  \midrule
  8 & Russell Westbrook & PG & Washington Wizards & 4.05\\
-  \midrule
  9 & Jayson Tatum & SF & Boston Celtics & 3.96\\
-  \midrule
  10 & Domanatas Sabonis & PF & Indiana Pacers & 3.21\\
@@
 
-As can be seen, one player rises above all others in both PAR and VORP. That player is Nikola Jokic of the 
-Denver Nuggets, and this "outlier" makes perfect sense, and helps show just how dominant his MVP 
-season was. Not only did Jokic average 26.4 points, 10.8 rebounds, and 8.3 assists per game, he was 
-doing it from the center position. Having a center that has the ability to perform in all aspects of the game, 
-even those that his position does not require, proves his value to his team, which is why his value is so 
-much higher in both the new PAR metric, and the accepted VORP metric. This logic applies to Nikola 
-Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as well. While they might not be 
-considered the best at their position, or an extremely elite player in the NBA, they are very versatile players, 
-that can do anything on the court, and thus they are rewarded with a high PAR value. This makes sense, as 
-without these players, a lot of the statistics their team accumulates are gone, so while they may not have as 
-much value in the grand scheme of the NBA, they were very much the most valuable players for their 
-teams. Another key thing to note is that some players, such as LeBron James, have a lower PAR than 
-expected, and this could be due to the fact that they played most frequently in a position that did not match 
-their skill set. LeBron James played primarily as a point guard, but his skillset matches that of a small 
-forward or power forward. Thus, his strengths are not adequately measured, as he is essentially being 
+As can be seen in \ref{tab:NBAtable}, one player rises above all others in 
+both PAR and VORP. 
+That player is Nikola Jokic of the 
+Denver Nuggets, and this "outlier" makes perfect sense, and helps show 
+just how dominant his MVP 
+season was. Not only did Jokic average 26.4 points, 10.8 rebounds, and 
+8.3 assists per game, he was 
+doing it from the center position. Having a center that has the ability to 
+perform in all aspects of the game, 
+even those that his position does not require, proves his value to his 
+team, which is why his value is so 
+much higher in both the new PAR metric, and the accepted VORP metric. 
+This logic applies to Nikola 
+Vucevic, Julius Randle, Russell Westbrook, and Domanatas Sabonis as 
+well. While they might not be 
+considered the best at their position, or an extremely elite player in the 
+NBA, they are very versatile players, 
+that can do anything on the court, and thus they are rewarded with a high 
+PAR value. This makes sense, as 
+without these players, a lot of the statistics their team accumulates are 
+gone, so while they may not have as 
+much value in the grand scheme of the NBA, they were very much the 
+most valuable players for their 
+teams. Another key thing to note is that some players, such as LeBron 
+James, have a lower PAR than 
+expected, and this could be due to the fact that they played most 
+frequently in a position that did not match 
+their skill set. LeBron James played primarily as a point guard, but his 
+skillset matches that of a small 
+forward or power forward. Thus, his strengths are not adequately 
+measured, as he is essentially being 
 played "out of position".
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Point Guards}
@@
  1 & Luka Doncic & Dallas Mavericks & 4.61\\
-  \midrule
  2 & Damian Lillard & Portland Trail Blazers & 4.47\\
-  \midrule
  3 & Stephen Curry & Golden State Warriors & 4.17\\
-  \midrule
  4 & Russell Westbrook & Washington Wizards & 4.05\\
-  \midrule
  5 & Trae Young & Atlanta Hawks & 2.69\\
-  \midrule
  6 & De'Aaron Fox & Sacramento Kings & 1.94\\
-  \midrule
  7 & Chris Paul & Phoenix Suns & 1.93\\
-  \midrule
  8 & Kyrie Irving & Brooklyn Nets & 1.74\\
-  \midrule
  9 & Dejounte Murray & San Antonio Spurs & 1.64\\
-  \midrule
  10 & Ja Morant & Memphis Grizzlies & 1.45\\
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Shooting Guards}
@@
  1 & Bradley Beal & Washington Wizards & 3.17\\
-  \midrule
  2 & Devin Booker & Phoenix Suns & 2.74\\
-  \midrule
  3 & Terry Rozier & Charlotte Hornets & 2.59\\
-  \midrule
  4 & Zach Lavine & Chicago Bulls & 2.29\\
-  \midrule
  5 & RJ Barrett & New York Knicks & 2.28\\
-  \midrule
  6 & Anthony Edwards & Minnesota Timberwolves & 2.22\\
-  \midrule
  7 & Jaylen Brown & Boston Celtics & 1.87\\
-  \midrule
  8 & Collin Sexton & Cleveland Cavaliers & 1.85\\
-  \midrule
  9 & Buddy Hield & Sacramento Kings & 1.72\\
-  \midrule
  10 & Norman Powell & Toronto Raptors & 1.37\\
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Small Forwards}
@@
  1 & Jayson Tatum & Boston Celtics & 3.96\\
-  \midrule
  2 & Khris Middleton & Milwaukee Bucks & 2.39\\
-  \midrule
  3 & Brandon Ingram & New Orleans Pelicans & 2.13\\
-  \midrule
  4 & Kawhi Leonard & Los Angeles Clippers & 1.58\\
-  \midrule
  5 & Paul George & Los Angeles Clippers & 1.44\\
-  \midrule
  6 & Michael Porter Jr. & Denver Nuggets & 1.42\\
-  \midrule
  7 & Jimmy Butler & Miami Heat & 1.41\\
-  \midrule
  8 & Bojan Bogdonavic & Utah Jazz & 1.35\\
-  \midrule
  9 & Mikal Bridges & Phoenix Suns & 1.19\\
-  \midrule
  10 & Jerami Grant & Detroit Pistons & 1.14\\
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Power Forwards}
@@
  1 & Julius Randle & New York Knicks & 6.49\\
-  \midrule
  2 & Giannis Antetokounmpo & Milwaukee Bucks & 4.21\\
-  \midrule
  3 & Domanatas Sabonis & Indiana Pacers & 3.21\\
-  \midrule
  4 & Zion Williamson & New Orleans Pelicans & 3.07\\
-  \midrule
  5 & Andrew Wiggins & Golden State Warriors & 2.26\\
-  \midrule
  6 & Demar Derozan & San Antonio Spurs & 1.88\\
-  \midrule
  7 & Tobias Harris & Philadelphia 76ers & 1.87\\
-  \midrule
  8 & Pascal Siakam & Toronto Raptors & 1.72\\
-  \midrule
  9 & John Collins & Atlanta Hawks & 1.35\\
-  \midrule
  10 & Harrison Barnes & Sacramento Kings & 1.11\\
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Centers}
@@
  1 & Nikola Jokic & Denver Nuggets & 7.69\\
-  \midrule
  2 & Nikola Vucevic & Orlando Magic & 6.55\\
-  \midrule
  3 & Rudy Gobert & Utah Jazz & 3.10\\
-  \midrule
  4 & Bam Adebayo & Miami Heat & 2.78\\
-  \midrule
  5 & Joel Embiid & Philadelphia 76ers & 2.26\\
-  \midrule
  6 & Clint Capela & Atlanta Hawks & 2.25\\
-  \midrule
  7 & DeAndre Ayton & Phoenix Suns & 2.11\\
-  \midrule
  8 & Jonas Valanciunas & Memphis Grizzlies & 1.98\\
-  \midrule
  9 & Karl-Anthony Towns & Minnesota Timberwolves & 1.82\\
-  \midrule
  10 & Kelly Olynyk & Miami Heat & 1.39\\
@@
 
-PAR will also be compared with the 4 accepted advanced metrics that were used as regressors in the 
-multiple regression on PAR. These include Player Efficiency Rating, Win Shares, Box Plus Minus, and 
-Value Over Replacement Player
+PAR will also be compared with the 4 accepted advanced metrics that 
+were used as regressors in the 
+multiple regression on PAR. These include Player Efficiency Rating, Win 
+Shares, Box Plus Minus, and 
+Value Over Replacement Player.
 
-\begin{figure}[H]
+\begin{figure}[tbp]
   \centering
@@
 
-\begin{figure}[H]
+\begin{figure}[tbp]
   \centering
@@
 
-It can be seen that the graphs of PAR and Win Shares, as well as PAR and Value Over Replacement Player 
-fit nicely, with a relatively positive and linear correlation. However, the graphs of PAR and Box Plus Minus, 
-as well as PAR and Player Efficiency Rating appear to have less of a linear distribution. This can be 
-attributed to the scaling methods of each statistic. Since Win Shares and Value Over Replacement Player 
-follow a similar scale, with a minimum slightly below 0, and a maximum somewhere in the range of 10, the 
-scales match, and each player's value of each metric fits similarly enough to form a linear distribution. 
-However, Box Plus Minus ranges from -40 to above 20, so we see the graph centered around 0, where the 
-majority of players fall, and going almost straight upwards based on their PAR value. Player Efficiency 
-Rating has a similar scale, so a similar effect is shown. In order to see how Points Above Replacement fits 
-in terms of all of these accepted metrics, a multiple regression will be run, with the 4 accepted metrics as 
+It can be seen in \ref{fig:Fig2} that the graphs of PAR and Win Shares, as 
+well as PAR 
+and Value Over Replacement Player in \ref{fig:Fig4}
+fit nicely, with a relatively positive and linear correlation. However, the 
+graphs of PAR and Box Plus Minus in. \ref{fig:Fig3}, 
+as well as PAR and Player Efficiency Rating in \ref{fig:Fig1} appear to 
+have less of a 
+linear distribution. This can be 
+attributed to the scaling methods of each statistic. Since Win Shares and 
+Value Over Replacement Player 
+follow a similar scale, with a minimum slightly below 0, and a maximum 
+somewhere in the range of 10, the 
+scales match, and each player's value of each metric fits similarly enough 
+to form a linear distribution in both \ref{fig:Fig2} and \ref{fig:Fig4}. 
+However, Box Plus Minus ranges from -40 to above 20, so we see the 
+graph of \ref{fig:Fig3} centered around 0, where the 
+majority of players fall, and going almost straight upwards based on their 
+PAR value. Player Efficiency 
+Rating has a similar scale, so a similar effect is shown in \ref{fig:Fig1}. In 
+order to see 
+how Points Above Replacement fits 
+in terms of all of these accepted metrics, a multiple regression will be run, 
+with the 4 accepted metrics as 
 regressors, and with PAR as the independent variable.
-\begin{figure}[H]
+
+\begin{table}[tbp]
+  \caption{Multiple Regression on PAR}
+  \label{tab:MultipleRegression}
 \centering
-  \includegraphics[scale = 0.6]{MultipleRegression}
-  \caption{Multiple Regression with Regressors PER, WS, BPM, and VORP and Independent Variable PAR}
-  \label{fig:Fig5}
-\end{figure}
+\begin{tabular}[t]{lccllll}
+  \toprule
+  Variable &  Estimate & Standard Error & P-Value\\
+  \midrule
+Intercept & -1.009821  & 0.144907 & 9.44 * e-12\\
+PER & 0.030409 & 0.009569 & 0.00157\\
+WS & 0.121319 & 0.023793 & 4.75 * e-7\\
+BPM & -0.056802 & 0.012889 & 1.27 * e-5\\
+VORP & 0.558947 & 0.048688 & Less Than 2 * e-16\\
+  \bottomrule
+\end{tabular}
+\end{table}
 
-The key statistic here is the adjusted R-squared value of 0.6974. This shows that 69.74 percent of variation 
-in PAR can be explained by these other 4 accepted metrics. This shows a clear correlation between PAR 
+Not included in the table \ref{tab:MultipleRegression} is the adjusted 
+R-squared 
+value of 0.6974. This 
+statistic is key, as it shows that 69.74 percent of variation 
+in PAR can be explained by these other 4 accepted metrics. This shows a 
+clear correlation between PAR 
 and the metrics, but also shows that PAR has something unique to offer.
@@
 % Talk about how it is in agreement with existing measures
-Ultimately, the goal of this statistic is to allow a reader to gauge a player's value to his team based on a 
-league average player. As previously stated, the metric is adjusted so that a league average player has a 
-PAR value of 0. Based on all other players' PAR values, we can create a sort of "legend", a rough guideline 
-for what a player's role will be based on the threshold his PAR value falls under.
+Ultimately, the goal of this statistic is to allow a reader to gauge a player's 
+value to his team based on a 
+league average player. As previously stated, the metric is adjusted so that 
+a league average player has a 
+PAR value of 0. Based on all other players' PAR values, we can create a 
+sort of "legend", a rough guideline 
+for what a player's role will be based on the threshold his PAR value falls 
+under.
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Legend}
@@
 Benchwarmer & Less than -0.43\\
-  \midrule
 Role Player & -0.43 to 0.08\\
-  \midrule
 Starter & 0.08 to 1.09\\
-  \midrule
 All-Star & 1.09 to 1.94\\
- \midrule
 Superstar & Greater than 1.94\\
@@
 
-This legend was calculated based on a quantile calculation of all PAR data. It is not an even distribution, as 
-it is assumed that there are many more benchwarmers in the NBA than there are superstars. Thus, 
-benchwarmers are defined as the bottom 50 percent of the league, as an NBA roster of about 15 players 
-will only give 7 or 8 players significant minutes. Players between the 50th and 75th percentile are defined 
-as role players, as they get significant minutes, but do not make an impact enough to be considered a solid 
-starter. This is where  a "league average" player is expected to fall, as 0 is contained in this part of the 
-legend, and 0 represents a league average player via this metric. Next, the 75th to 90th percentile are 
-defined as starters, because only 5 players can start a game, and, more often than not, a team only has 3 
-or 4 players who are guaranteed starters. 90th to 95th percentiles represent all-stars, as that is clearly a 
-very prestigious area to be a part of. Lastly, it is assumed that only the top 5 percent of players in the 
-league can be deemed "superstars", so they comprise the 95th to 100th percentile of the NBA. By this 
-method, it is felt that a more realistic legend for PAR has been created as opposed to just breaking up the 
+This legend in \ref{tab:PARLegend} was calculated based on a quantile 
+calculation of all PAR 
+data. It is not an even distribution, as 
+it is assumed that there are many more benchwarmers in the NBA than 
+there are superstars. Thus, 
+benchwarmers are defined as the bottom 50 percent of the league, as an 
+NBA roster of about 15 players 
+will only give 7 or 8 players significant minutes. Players between the 50th 
+and 75th percentile are defined 
+as role players, as they get significant minutes, but do not make an impact 
+enough to be considered a solid 
+starter. This is where  a "league average" player is expected to fall, as 0 is 
+contained in this part of the 
+legend, and 0 represents a league average player via this metric. Next, 
+the 75th to 90th percentile are 
+defined as starters, because only 5 players can start a game, and, more 
+often than not, a team only has 3 
+or 4 players who are guaranteed starters. 90th to 95th percentiles 
+represent all-stars, as that is clearly a 
+very prestigious area to be a part of. Lastly, it is assumed that only the top 
+5 percent of players in the 
+league can be deemed "superstars", so they comprise the 95th to 100th 
+percentile of the NBA. By this 
+method, it is felt that a more realistic legend for PAR has been created as 
+opposed to just breaking up the 
 data evenly into 5 groups.
@@
 \bibliographystyle{chicago}
-\bibliography{citations.bib}
-\section*{Acknowledgements}
-The authors thank the University of Connecticut and the UConn Department of Statistics.
+\bibliography{citations}
+
+%\section*{Acknowledgements}
+%The authors thank the University of Connecticut and the UConn Department of Statistics.
 
@@
 \section*{About the Student Author}
-Brian Krikorian plans to graduate in May 2022 from the University of Connecticut, with a Bachelor's of Science in Data Science, and a minor in Computer Science.
+Brian Krikorian plans to graduate in May 2022 from the University of 
+Connecticut, with a Bachelor's of Science in Data Science, and a minor in 
+Computer Science.
 
 % The Press Summary section is NOT optional.  Write a paragraph describing the paper in a manner suitable for the press; see previous journal editions for examples.
-\section*{Press Summary}
+
+%\section*{Press Summary}
 

### 2022-04-14 Manuscript/Manuscript.tex
quick comments

@@
 adjust a player's importance based on what is expected of their position. 
-The coefficients for each position are listed in table 
-\ref{tab:Coefficientstable}. Coefficients are subjective, but were changed 
+The coefficients for each position are listed in
+Table~\ref{tab:Coefficientstable}. Coefficients are subjective, but were changed
 to have a constant scale by position, and create a PAR scale that lined up 
@@
 NBA. The formula for PAR is listed below.
-
 \begin{equation}
@@
 \end{equation}
-
-\ref{eq:PAR} gives a good idea of how many points a player accounts for 
+Equation~\eqref{eq:PAR} gives a good idea of how many points a player accounts for 
 during a 
@@
 
-As can be seen in \ref{tab:NBAtable}, one player rises above all others in 
+\jy{Refer to a table or figure like this:}
+As can be seen in Table~\ref{tab:NBAtable}, one player rises above all others in 
 both PAR and VORP. 
@@
 played "out of position".
+
+\jy{The two tables for guards could be combined into one; and the same for
+  forwards}
 
@@
 
+\jy{don't scale figures; control their sizes in R when generating them;}
 \begin{figure}[tbp]
   \centering
-  \includegraphics[scale = 0.6]{PERvsPAR}
+  \includegraphics[width=\textwidth]{PERvsPAR}
   \caption{Player Efficiency Ratings (x) vs. Points Above Replacement (y)}
@@
 
-Not included in the table \ref{tab:MultipleRegression} is the adjusted 
+\jy{two many digits in this table}
+Not included in the Table~\ref{tab:MultipleRegression} is the adjusted 
 R-squared 

### 2022-04-19 Manuscript/Manuscript.tex
Add files via upload

--- 2022-04-14 Manuscript/Manuscript.tex
@@
 adjust a player's importance based on what is expected of their position. 
-The coefficients for each position are listed in table 
+The coefficients for each position are listed in Table~
 \ref{tab:Coefficientstable}. Coefficients are subjective, but were changed 
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
@@
 
-\ref{eq:PAR} gives a good idea of how many points a player accounts for 
+Equation~\ref{eq:PAR} gives a good idea of how many points a player accounts for 
 during a 
@@
 
-As can be seen in \ref{tab:NBAtable}, one player rises above all others in 
+As can be seen in Table~\ref{tab:NBAtable}, one player rises above all others in 
 both PAR and VORP. 
@@
 
-\begin{figure}[tbp]
+\begin{figure}[H]
   \centering
-  \includegraphics[scale = 0.6]{PERvsPAR}
+  \includegraphics[width=\textwidth]{PERvsPAR}
   \caption{Player Efficiency Ratings (x) vs. Points Above Replacement (y)}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[H]
   \centering
-  \includegraphics[scale = 0.6]{WSvsPAR}
+  \includegraphics[width=\textwidth]{WSvsPAR}
   \caption{Win Shares (x) vs. Points Above Replacement (y)}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[H]
   \centering
-  \includegraphics[scale = 0.6]{BPMvsPAR}
+  \includegraphics[width=\textwidth]{BPMvsPAR}
   \caption{Box Plus Minus (x) vs. Points Above Replacement (y)}
@@
 
-\begin{figure}[tbp]
+\begin{figure}[H]
   \centering
-  \includegraphics[scale = 0.6]{VORPvsPAR}
+  \includegraphics[width=\textwidth]{VORPvsPAR}
   \caption{Value Over Replacement Player (x) vs. Points Above Replacement (y)}
@@
 
-It can be seen in \ref{fig:Fig2} that the graphs of PAR and Win Shares, as 
+It can be seen in Figure~\ref{fig:Fig2} that the graphs of PAR and Win Shares, as 
 well as PAR 
-and Value Over Replacement Player in \ref{fig:Fig4}
+and Value Over Replacement Player in Figure~\ref{fig:Fig4}
 fit nicely, with a relatively positive and linear correlation. However, the 
-graphs of PAR and Box Plus Minus in. \ref{fig:Fig3}, 
-as well as PAR and Player Efficiency Rating in \ref{fig:Fig1} appear to 
+graphs of PAR and Box Plus Minus in. Figure~\ref{fig:Fig3}, 
+as well as PAR and Player Efficiency Rating in Figure~\ref{fig:Fig1} appear to 
 have less of a 
@@
 scales match, and each player's value of each metric fits similarly enough 
-to form a linear distribution in both \ref{fig:Fig2} and \ref{fig:Fig4}. 
+to form a linear distribution in both Figure~\ref{fig:Fig2} and Figure~\ref{fig:Fig4}. 
 However, Box Plus Minus ranges from -40 to above 20, so we see the 
-graph of \ref{fig:Fig3} centered around 0, where the 
+graph of Figure~\ref{fig:Fig3} centered around 0, where the 
 majority of players fall, and going almost straight upwards based on their 
 PAR value. Player Efficiency 
-Rating has a similar scale, so a similar effect is shown in \ref{fig:Fig1}. In 
+Rating has a similar scale, so a similar effect is shown in Figure~\ref{fig:Fig1}. In 
 order to see 
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{Multiple Regression on PAR}
@@
 
-Not included in the table \ref{tab:MultipleRegression} is the adjusted 
+Not included in the table Table~\ref{tab:MultipleRegression} is the adjusted 
 R-squared 
@@
 
-\begin{table}[tbp]
+\begin{table}[H]
   \caption{PAR Legend}
@@
 
-This legend in \ref{tab:PARLegend} was calculated based on a quantile 
+This legend in Table~\ref{tab:PARLegend} was calculated based on a quantile 
 calculation of all PAR 

### 2022-04-21 Code/NBAPARCode.Rmd
Add files via upload

@@
 ```{r data, include=FALSE}
-league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/League.csv', stringsAsFactors = TRUE, header = TRUE)
+league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
 ```
@@
 summary(PARandVORP)
-plot(league$VORP, scaledPAR)
 
@@
 plot(multipleRegression)
+
+legend<-quantile(scaledPAR, probs = c(0, 0.5, 0.75, 0.9, 0.95, 1))
+print("Breaking PAR into 5 groups")
+print(legend)
+
+plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR", main = "Value Over Replacement Player vs. Points Above Replacement")
+plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR", main = "Win Shares vs. Points Above Replacement")
+plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR", main = "Box Plus Minus vs. Points Above Replacement")
+plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR", main = "Player Efficiency Rating vs. Points Above Replacement")
 ```

### 2022-04-21 Code/NBAPARCode.Rmd
Add files via upload

@@
 
-plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR", main = "Value Over Replacement Player vs. Points Above Replacement")
-plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR", main = "Win Shares vs. Points Above Replacement")
-plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR", main = "Box Plus Minus vs. Points Above Replacement")
-plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR", main = "Player Efficiency Rating vs. Points Above Replacement")
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/VORPvsPAR.pdf", width = 6, height = 6)
+plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/WSvsPAR.pdf", width = 6, height = 6)
+plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/BPMvsPAR.pdf", width = 6, height = 6)
+plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/PERvsPAR.pdf", width = 6, height = 6)
+plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR")
+dev.off()
 ```

### 2022-04-21 Manuscript/Manuscript.tex
Add files via upload

@@
 
-\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
-\captionsetup{labelformat=simple, labelsep=period}
+%\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
+%\captionsetup{labelformat=simple, labelsep=period}
 %\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
@@
 gains or loses by missing a certain player, and thus having to replace him 
-with one who is "league 
-average". The statistic is standardized and adjusted by both position and 
+with one who is ``league 
+average''. The statistic is standardized and adjusted by both position and 
 value to a player's given team. 
@@
 collected from the Basketball Reference 
-website, as well as each team's total points throughout the course of the season \citep{BasketballReference}. From the basic statistics, 4 metrics were 
+website, as well as each team's total points throughout the course of the 
+season \citep{BasketballReference}. From the basic statistics, 4 metrics 
+were 
 created in order to calculate PAR. 
@@
 hitting, base running, fielding, 
-and so forth. The subjectivity is in the coefficients chosen to scale 
+and so forth \citep{BaseballWAR}. The subjectivity is in the coefficients 
+chosen to scale 
 statistics which impact Offensive and 
@@
 player adds for his team, and how 
-many he prevents the other team from scoring. Using the basic offensive 
+many he prevents the other team from scoring.
+
+Using the basic offensive 
 statistics of Effective Field Goal 
@@
 respectively, of 4, 3.5, 3, 2.5, and 2.
+
 The coefficient by position method is one similar to that of Box Plus 
-Minus, another advanced NBA metric. 
+Minus, another advanced NBA metric \citep{BasketballReferenceBPM}. 
 The position a player was assigned for the calculation was the position 
@@
 sum was taken to give Offensive 
-Points. The exact same method was applied to the Defensive Points 
+Points.
+
+The exact same method was applied to the Defensive Points 
 calculation, but used the basic 
@@
 adjust a player's importance based on what is expected of their position.
+
 The coefficients for each position are listed in Table~
@@
 to have a constant scale by position, and create a PAR scale that lined up 
-closely with other advanced metrics.
+closely with other advanced metrics. This coefficient matrix could be 
+looked at as an optimization problem, where coefficients by position are 
+changed to achieve as high of a correlation with other advanced metrics 
+as possible. However, a constant scale by position and a relatively high 
+correlation to other metrics shows uniqueness in the statistic but also 
+validity.
 
@@
 \centering
-\begin{tabular}[t]{lccllll}
+\begin{tabular}[t]{lcccccc}
   \toprule
@@
  Points & 2 & 2 & 2 & 2 & 2\\
- Turnovers & -5 & -4.5 & -4 & -3.5 & -3\\
+ Turnovers & $-5$ & $-4.5$ & $-4$ & $-3.5$ & $-3$\\
  Defensive Rebounds & 2 & 2.5 & 3 & 3.5 & 4\\
@@
  Blocks & 3 & 3.5 & 4 & 4.5 & 5\\
- Personal Fouls & -3 & -3 & -3 & -3 & -3\\
+ Personal Fouls & $-3$ & $-3$ & $-3$ & $-3$ & $-3$\\
   \bottomrule
@@
 team the player had played the most minutes for was assigned as his 
-team. The Team Adjustment statistic 
+team.
+
+The Team Adjustment statistic 
 is then calculated by taking the total minutes a player was on the court 
@@
 100 percent of his team's points, the result is a number between 0 and 1.
+
 A similar adjustment is also used 
@@
 
-Equation~\ref{eq:PAR} gives a good idea of how many points a player accounts for 
+Equation~\ref{eq:PAR} gives a good idea of how many points a player 
+accounts for 
 during a 
@@
 created a new NBA player metric, 
-Points Above Replacement, PAR. All of the calculations, multiple regression, and graphs were created using R \citep{R}.
+Points Above Replacement, PAR. All of the calculations, multiple 
+regression, and graphs were created using R \citep{R}.
 
@@
 
-As can be seen in Table~\ref{tab:NBAtable}, one player rises above all others in 
+As can be seen in Table~\ref{tab:NBAtable}, one player rises above all 
+others in 
 both PAR and VORP. 
 That player is Nikola Jokic of the 
-Denver Nuggets, and this "outlier" makes perfect sense, and helps show 
+Denver Nuggets, and this ``outlier'' makes perfect sense, and helps show 
 just how dominant his MVP 
@@
 measured, as he is essentially being 
-played "out of position".
+played ``out of position''.
 
@@
 
-It can be seen in Figure~\ref{fig:Fig2} that the graphs of PAR and Win Shares, as 
+It can be seen in Figure~\ref{fig:Fig2} that the graphs of PAR and Win 
+Shares, as 
 well as PAR 
@@
 graphs of PAR and Box Plus Minus in. Figure~\ref{fig:Fig3}, 
-as well as PAR and Player Efficiency Rating in Figure~\ref{fig:Fig1} appear to 
+as well as PAR and Player Efficiency Rating in Figure~\ref{fig:Fig1} 
+appear to 
 have less of a 
@@
 scales match, and each player's value of each metric fits similarly enough 
-to form a linear distribution in both Figure~\ref{fig:Fig2} and Figure~\ref{fig:Fig4}. 
+to form a linear distribution in both Figure~\ref{fig:Fig2} and 
+Figure~\ref{fig:Fig4}. 
 However, Box Plus Minus ranges from -40 to above 20, so we see the 
@@
 PAR value. Player Efficiency 
-Rating has a similar scale, so a similar effect is shown in Figure~\ref{fig:Fig1}. In 
+Rating has a similar scale, so a similar effect is shown in 
+Figure~\ref{fig:Fig1}. In 
 order to see 
@@
   \midrule
-Intercept & -1.009821  & 0.144907 & 9.44 * e-12\\
-PER & 0.030409 & 0.009569 & 0.00157\\
-WS & 0.121319 & 0.023793 & 4.75 * e-7\\
-BPM & -0.056802 & 0.012889 & 1.27 * e-5\\
-VORP & 0.558947 & 0.048688 & Less Than 2 * e-16\\
+Intercept & $-1.009$  & 0.145 & $9.44 \times 10^{-12}$\\
+PER & 0.030 & 0.009 & 0.002\\
+WS & 0.121 & 0.024 & $4.75 \times 10^{-7}$\\
+BPM & $-0.057$ & 0.013 & $1.27 \times 10^{-5}$\\
+VORP & 0.559 & 0.049 & Less Than $2 \times 10^{-16}$\\
   \bottomrule
@@
 
-Not included in the table Table~\ref{tab:MultipleRegression} is the adjusted 
-R-squared 
-value of 0.6974. This 
+In Table~\ref{tab:MultipleRegression} an adjusted R-squared value of 
+0.6974 is shown, along with an SER of 0.5501. The adjusted R-squared
 statistic is key, as it shows that 69.74 percent of variation 
@@
 PAR value of 0. Based on all other players' PAR values, we can create a 
-sort of "legend", a rough guideline 
+sort of ``legend'', a rough guideline 
 for what a player's role will be based on the threshold his PAR value falls 
@@
   \midrule
-Benchwarmer & Less than -0.43\\
-Role Player & -0.43 to 0.08\\
+Benchwarmer & Less than $-0.43$\\
+Role Player & $-0.43$ to 0.08\\
 Starter & 0.08 to 1.09\\
@@
 
-This legend in Table~\ref{tab:PARLegend} was calculated based on a quantile 
+This legend in Table~\ref{tab:PARLegend} was calculated based on a 
+quantile 
 calculation of all PAR 
@@
 enough to be considered a solid 
-starter. This is where  a "league average" player is expected to fall, as 0 is 
+starter. This is where  a `league average'' player is expected to fall, as 0 is 
 contained in this part of the 
@@
 often than not, a team only has 3 
-or 4 players who are guaranteed starters. 90th to 95th percentiles 
+or 4 players who are guaranteed starters. The 90th to 95th percentiles 
 represent all-stars, as that is clearly a 
@@
 5 percent of players in the 
-league can be deemed "superstars", so they comprise the 95th to 100th 
+league can be deemed ``superstars'', so they comprise the 95th to 100th 
 percentile of the NBA. By this 

### 2022-04-26 Manuscript/Manuscript.tex
Add files via upload

@@
 
+\begin{equation}
+\label{eq:TeamAdjustment}
+  \frac{\text{Minutes Played}}{3456} \times
+  \frac{\text{Points}}{\text{Team Total Points}}.
+\end{equation}
+
+Creating the ``Team Adjustment'' statistic via 
+equation~\ref{eq:TeamAdjustment} has then successfully adjusted a 
+player's statistics to his specific team.
+
 A similar adjustment is also used 
@@
 
-Once all supporting statistics of PAR have been created, all that is left to 
+\begin{equation}
+\label{eq:PointsPerWin}
+ \frac{\text{Offensive Points} + \text{Defensive Points}} {\text{Minutes 
+Played}} + 2160.
+\end{equation}
+
+By creating the ``Points Per Win'' statistic, equation~\ref{eq:PointsPerWin} 
+has thus scaled down the statistic based 
+on how many points are in an average win, similar to Runs Per Win in 
+WAR. The constant of 2,160 would change to 2,460 for an 82-game 
+season, for a typical NBA season.
+
+Finally, once all supporting statistics of PAR have been created, all that is left to 
 do is combine them to achieve our PAR values for each player in the 
@@
 last step is to standardize this 
-PAR statistic, so that the mean is 0, and the standard deviation is 1. 
+ rough PAR statistic, so that the mean is 0, and the standard deviation is 
+1. 
 Logically, this helps the idea of the 
@@
 
+The concept of assigning value to a player based on how many points he 
+contributes to his team is the main goal of this statistic. By taking the 
+calculation of WAR from baseball, which is how many wins a player 
+contributes to his team, and adjusting it for the sport of basketball, and 
+points rather than wins, it is felt that the goal is successfully achieved. The 
+scaling of the data around the mean allows a ``replacement level'' player 
+to contribute exactly 0 points to his team, and the rest of the league is 
+compared to that. The team adjustment is a key one as well, as, 
+depending on what team a player plays for, his value will change, 
+sometimes even drastically. Further research would need to be done, 
+such as comparing PAR's estimation with actual point differentials when 
+an entire roster aside from a certain player plays, but for the most part, 
+the original goal of creating this statistic is achieved.
+
+As can be seen from the 
+Table~\ref{tab:MultipleRegression}, it is in relative agreement with many 
+other accepted statistics, and even takes some ideas from the calculation 
+of those statistics. However, at the same time, it is unique enough that it 
+introduces a brand new outlook to the advanced metrics subject. Other 
+statistics look for other ways to value a player, which is where the 
+variation comes into play, but for the most part, elite players are valued as 
+such through PAR, which is how it is known that the statistic holds.
+
+There are a few limitations to discuss in the calculation of PAR. Firstly, the 
+subjectivity in calculating the coefficients for Offensive and Defensive 
+Points, as seen in Table~\ref{tab:Coefficientstable}, could be changed to 
+any numbers to serve whatever purpose one is looking for. However, in 
+baseball's WAR, this is the subjective part of the statistic that causes 
+there to realistically be many different kinds of WAR, despite them all 
+being the same statistic. The coefficients could be tweaked to serve a 
+number of different purposes. Further tests could also be done to test the 
+validity of PAR in practice. This could help a final score estimation model 
+in the future for the purpose of season simulations, sports betting, and a 
+number of other purposes. The sample size of 1 season makes this 
+difficult, so calculations across multiple seasons, and future ones would 
+help this discussion. However, PAR seems to provide a decent estimate of 
+a player's value to his team, which is especially shown through its relation 
+to VORP and BPM, which are the advanced metrics with goals that are 
+most similar to that of PAR.
+
 \bibliographystyle{chicago}

### 2022-04-26 Manuscript/Manuscript.tex
Add files via upload

@@
 Creating the ``Team Adjustment'' statistic via 
-equation~\ref{eq:TeamAdjustment} has then successfully adjusted a 
+Equation~\eqref{eq:TeamAdjustment} has then successfully adjusted a 
 player's statistics to his specific team.
@@
 
-By creating the ``Points Per Win'' statistic, equation~\ref{eq:PointsPerWin} 
+By creating the ``Points Per Win'' statistic, Equation~\eqref{eq:PointsPerWin} 
 has thus scaled down the statistic based 
@@
 
-Equation~\ref{eq:PAR} gives a good idea of how many points a player 
+Equation~\eqref{eq:PAR} gives a good idea of how many points a player 
 accounts for 

### 2022-04-26 Code/NBAPARCode.Rmd
Add files via upload

--- 2022-04-21 Code/NBAPARCode.Rmd
@@
 
-plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR", main = "Value Over Replacement Player vs. Points Above Replacement")
-plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR", main = "Win Shares vs. Points Above Replacement")
-plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR", main = "Box Plus Minus vs. Points Above Replacement")
-plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR", main = "Player Efficiency Rating vs. Points Above Replacement")
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/VORPvsPAR.pdf", width = 6, height = 4)
+plot(league$VORP, scaledPAR, xlab = "VORP", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/WSvsPAR.pdf", width = 6, height = 3.5)
+plot(league$WS, scaledPAR,  xlab = "WS", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/BPMvsPAR.pdf", width = 6, height = 3.5)
+plot(league$BPM, scaledPAR, xlab = "BPM", ylab = "PAR")
+dev.off()
+
+pdf(file= "/Users/briankrikorian/Documents/GitHub/Spring2022Thesis/Manuscript/figs/PERvsPAR.pdf", width = 6, height = 4)
+plot(league$PER, scaledPAR, xlab = "PER", ylab = "PAR")
+dev.off()
 ```

### 2022-04-27 Code/NBAPARCode.Rmd
use relative path in code for portability

@@
 ```{r data, include=FALSE}
-league <- read.csv(file = '~/Documents/GitHub/Spring2022Thesis/Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
+## use relative path for portability
+league <- read.csv(file = '../Data/League.csv', stringsAsFactors = TRUE, header = TRUE)
 ```

### 2022-06-02 Manuscript/Manuscript.tex
set up for jsa and comments

@@
-\documentclass[12pt]{article}
+\documentclass[titlepage, 12pt]{article}
 \usepackage[margin=1in]{geometry}
@@
 
-\usepackage{xr}
-
 % remove left indentation in itemize
@@
 
-\usepackage{geometry}
-\geometry{vmargin={1in,1in}, hmargin={.75in, .75in}}
-
-%\usepackage[labelfont={footnotesize,bf} , textfont=footnotesize]{caption}
-%\captionsetup{labelformat=simple, labelsep=period}
-%\newcommand\num{\addtocounter{equation}{1}\tag{\theequation}}
-%\renewcommand{\theequation}{\arabic{equation}}
-%\makeatletter
-%\renewcommand\tagform@[1]{\maketag@@@ {\ignorespaces {\footnotesize{\textbf{Equation}}} #1.\unskip \@@italiccorr }}
 \makeatother
@@
 
+\usepackage[]{lineno}
+\linenumbers*[1]
+%% patches to make lineno work better with amsmath
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+	\expandafter\let\csname old#1\expandafter\endcsname\csname 
+	#1\endcsname
+	\expandafter\let\csname oldend#1\expandafter\endcsname\csname 
+	end#1\endcsname
+	\renewenvironment{#1}%
+	{\linenomath\csname old#1\endcsname}%
+	{\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+	\patchAmsMathEnvironmentForLineno{#1}%
+	\patchAmsMathEnvironmentForLineno{#1*}}%
+\AtBeginDocument{%
+	\patchBothAmsMathEnvironmentsForLineno{equation}%
+	\patchBothAmsMathEnvironmentsForLineno{align}%
+	\patchBothAmsMathEnvironmentsForLineno{flalign}%
+	\patchBothAmsMathEnvironmentsForLineno{alignat}%
+	\patchBothAmsMathEnvironmentsForLineno{gather}%
+	\patchBothAmsMathEnvironmentsForLineno{multline}%
+}
+
 \quotingsetup{leftmargin = 0pt}
@@
 Department of Statistics, University of Connecticut, Storrs, CT  \\  \medskip 
-Students: brian.krikorian@uconn.edu* \\
-Mentor: jun.yan@uconn.edu 
+brian.krikorian@uconn.edu* \\
+ jun.yan@uconn.edu 
 }
@@
 \begin{document}
+\maketitle
 
-\begin{titlepage}
-   \begin{center}
-       \vspace*{1cm}
-       \Huge
-       \textbf{Points Above Replacement}
-
-       \Large
-       \vspace{0.5cm}
-        A New NBA Metric to Evaluate Player Performance
-
-       \vspace{1.5cm}
-
-       \textbf{Brian Krikorian}
-
-       \vfill
-
-       \includegraphics[width=0.4\textwidth]{UCONNwordmark}
-
-       \vfill
-
-       Mentor: Jun Yan\\
-       Data Science
-
-       \vspace{0.8cm}
-
-       \includegraphics[width=0.4\textwidth]{UCONNoakleaf}
-
-        \Large    
-       Department of Statistics\\
-       University of Connecticut\\
-       Storrs, CT\\
-
-   \end{center}
-\end{titlepage}
-% Abstracts are required.
-\section*{Abstract}
+\begin{abstract}
 In attempting to predict the score of an NBA game, players who are 
@@
 
-% Keywords are required.
-\section*{Keywords} 
+\bigskip
+\noindent{\sc Keywords}:
 Analytics; Basketball; Player Value; Sports Data; Statistics; 
-\vspace{.12 in}
-% Start the main part of the manuscript here.
-% Comment out section headings if inappropriate to your discipline.
-% If you add additional section or subsection headings, use an asterisk * to avoid numbering.
+\end{abstract}
+
+\jy{Read some articles in JSA to get a feeling of their styles.}
+
+\jy{Why is the minimum of PAR just below zero? Does this mean there is barely
+  any players below average?}
+
+\jy{Equations should be part of sentences.}
+
+\jy{The references are weak at this point.}
 
 \section{Introduction}
+
 %Why is this important/interesting? What has been done before on this topic? (Literature Review) What am I introducing that is new? 
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{Coefficients for Each Statistic in Offensive and Defensive Points}
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Values from all Point Guards}
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{Multiple Regression on PAR}
@@
 
-\begin{table}[H]
+\begin{table}[tbp]
   \caption{PAR Legend}
@@
 % If there is more than one student author, you must move the comment below.
-\section*{About the Student Author}
-Brian Krikorian plans to graduate in May 2022 from the University of 
-Connecticut, with a Bachelor's of Science in Data Science, and a minor in 
-Computer Science.
+% \section*{About the Student Author}
+% Brian Krikorian plans to graduate in May 2022 from the University of 
+% Connecticut, with a Bachelor's of Science in Data Science, and a minor in 
+% Computer Science.
 

### 2022-06-13 Manuscript/Manuscript.tex
Add files via upload

--- 2022-04-26 Manuscript/Manuscript.tex
@@
 measured, as he is essentially being 
-played ``out of position''.
+played ``out of position''. Another thing to note is that the lowest values 
+of PAR do not fall very fall below 0, but the highest values reach closer 
+to 10. This is due to the fact that PAR is related to minutes played. If a 
+player has a below average skillset, they will not receive as many 
+minutes, and thus their absence doesn't help their team a massive 
+amount, although it certainly does help.
 
@@
 \section*{About the Student Author}
-Brian Krikorian plans to graduate in May 2022 from the University of 
-Connecticut, with a Bachelor's of Science in Data Science, and a minor in 
-Computer Science.
+Brian Krikorian graduated in May 2022 from the University of 
+Connecticut, with a Bachelor's of Science in Data Science, and a minor 
+in Computer Science.
 
